### 2014-11-19 Draft.tex
intro

\documentclass[prb,preprint]{revtex4-1} 
% The line above defines the type of LaTeX document.
% Note that AJP uses the same style as Phys. Rev. B (prb).

% The % character begins a comment, which continues to the end of the line.

\usepackage{amsmath}  % needed for \tfrac, \bmatrix, etc.
\usepackage{amsfonts} % needed for bold Greek, Fraktur, and blackboard bold
\usepackage{graphicx} % needed for figures

\begin{document}

% Be sure to use the \title, \author, \affiliation, and \abstract macros
% to format your title page.  Don't use lower-level macros to  manually
% adjust the fonts and centering.

\title{Critical Temperature of Superconductors YBCO and BSCCO}
% In a long title you can use \\ to force a line break at a certain location.

\author{}
\affiliation{}

% optional second address
% If there were a second author at the same address, we would put another 
% \author{} statement here.  Don't combine multiple authors in a single
% \author statement.

\author{Frances Yang}
\affiliation{Department of Physics, Smith College, Northampton, MA 01063}

% See the REVTeX documentation for more examples of author and affiliation lists.

\date{\today}

\begin{abstract}
This article explains and illustrates the use of \LaTeX\ in preparing manuscripts
for submission to the American Journal of Physics (AJP). While it is not a
comprehensive reference, we hope it will suffice for the needs of most
AJP authors.
\end{abstract}
% AJP requires an abstract for all regular article submissions.
% Abstracts are optional for submissions to the "Notes and Discussions" section.

\maketitle % title page is now complete

\section{Introduction} % Section titles are automatically converted to all-caps.
% Section numbering is automatic.
In 1911, certain types of metals at temperatures around 10 K were found to exhibit superconductivity, that is, their electrical resistance became zero. 
The temperature at which this loss of resistance occurs is called the critical temperature.

\section{Ordinary text and paragraphs}

To typeset a paragraph of ordinary text, just type the text in your source
file like this. Put line breaks
wherever
you
want, and don't      worry      about      extra      spaces      between      words, which \LaTeX\ will ignore.  You can almost always trust \LaTeX\ to make your paragraphs look good, with neatly justified margins.  % Long lines of text are fine, since most editing programs will wrap them automatically.

To start a new paragraph, just leave a blank line in your source file.

A few punctuation characters require special treatment in \LaTeX. There 
are no ``smart quotes,'' so you need to use the left-quote key (at the 
top-left corner of the keyboard) for a left quote, and the ordinary apostrophe
key (next to the semi-colon) for a right quote. Hit either key twice for double
quotes, which are standard in American English.  Don't use shift-apostrophe
to make double quotes.  Use single quotes when they're nested inside a 
double-quoted quotation.  When a period or comma belongs at the end of
a quotation, put it inside the quotes---even if it's not part of what you're
quoting.\cite{nevermindlogic}

Your fingers also need to distinguish between a hyphen (used for
multi-word adjectives and for hyphenated names like Lennard-Jones), an 
en-dash (formed by typing two consecutive hyphens, and used for ranges 
of numbers like 1--100), and an em-dash (formed out of three consecutive
hyphens and used as an attention-getting punctuation symbol---preferably 
not too often).

Some non-alphanumeric symbols like \$, \&, and \% have special meanings 
in a \LaTeX\ source file, so if you want these symbols to appear in the output, 
you need to precede them with a backslash.

There are also special codes for generating the various accents
that can appear in foreign-language words and names, such as Amp\`ere
and Schr\"odinger.\cite{FontEncodingComment}

You can switch to \textit{italic}, \textbf{bold}, and \texttt{typewriter} fonts
when necessary. Use curly braces to enclose the text that is to appear in 
the special font. In general, \LaTeX\ uses curly braces to group characters 
together for some common transformation.

Notice that any word or symbol preceded by the backslash character is
a special instruction to \LaTeX, typically used to produce a special 
symbol or to modify the typeset output in some way. These instructions 
are also called \textit{control sequences} or \textit{macros}.  
After you've used \LaTeX\ for a while, the little finger of your right 
hand will be really good at finding the backslash and curly-brace keys.

\section{Math symbols}

To type mathematical symbols and expressions within a paragraph, put
them between \$ signs, which indicate \textit{math mode}: $ab + 2c/d = e-3f$.
\LaTeX\ ignores spaces in math mode, using its own algorithms to determine
the right amount of space between symbols.  Notice that an ordinary letter 
like~$x$, when used in math mode, is automatically typeset in italics. 
This is why you need to use math mode for all mathematical
expressions (except plain numerals), even when they don't contain any 
special symbols.  But don't use math mode to italicize ordinary \textit{words}.

Besides ordinary letters and numerals and common arithmetic symbols, math 
mode provides a host of other characters that you can access via control 
sequences.\cite{wikimathpage} These include Greek letters like $\pi$ and 
$\Delta$ (note capitalization), symbols for operations and relations such 
as $\cdot$, $\times$, $\pm$, $\gg$, $\leq$, $\sim$, $\approx$, $\propto$, 
and $\rightarrow$, and special symbols like $\nabla$, $\partial$, $\infty$, 
and~$\hbar$. You can decorate symbols with dots ($\dot x$ or $\ddot x$), 
arrows ($\vec\mu$), bars ($\bar x$ or $\overline m$), hats ($\hat x$), 
tildes ($\tilde f$ or $\widetilde w$), and radicals ($\sqrt\pi$, $\sqrt{2/3}$).
Parentheses and square brackets require no special keystrokes, but you
can also make curly braces and angle brackets: $\{\langle\ \cdots\ \rangle\}$.

To make subscripts and superscripts, use the underscore and caret 
(circumflex) symbols on your keyboard: $x^\mu$, $g_{\mu\nu}$, $\delta^i_j$, 
$\epsilon^{ijk}$.  Notice that you need to put the subscript or superscript 
in curly braces if it's longer than one character (or one control sequence). 
You can even make nested subscripts and superscripts, as in $e^{-x^2}$.  
If a subscript consists of an entire word or word-like abbreviation, 
we usually put it in plain Roman type: $x_\textrm{max}$.  If you need to 
put a subscript or superscript \textit{before} a symbol, use an empty
set of curly braces: ${}^{235}_{\ 92}\textrm{U}$. (Notice the trick of using 
backslash-space put a space before the 92.)

\newcommand{\bE}{\mathbf{E}}   % defines the abbreviation \bE, used below

To make boldface letters you use the \verb/\mathbf/ control sequence, as in
$\nabla\times\mathbf{E} = -\partial\mathbf{B}/\partial t$.  For bold Greek
letters like $\boldsymbol{\omega}$, you need to use \verb/\boldsymbol/
instead.  You can also use calligraphic ($\mathcal{E}$), Fraktur 
($\mathfrak{D}$), and blackboard bold ($\mathbb{R}$) fonts, if you need them. 
If you'll be using a symbol in a special font repeatedly, you can save 
some keystrokes by defining an abbreviation for it; for example, the 
definition \verb/\newcommand{\bE}{\mathbf{E}}/ allows you to type simply 
\verb/\bE/ to get $\bE$.

Unit abbreviations, as in $1~\mathrm{eV} = 1.6\times10^{-19}~\mathrm{J}$,
should be in the plain Roman font, not italics.  You can access this font
from math mode using \verb/\mathrm/. For function names like $\sin\theta$, 
$\exp x$, and $\ln N!$, \LaTeX\ provides special control sequences, 
which you should use instead of \verb/\mathrm/ whenever possible because
they work better with \LaTeX's automatic spacing algorithms.

But \LaTeX\ doesn't always get the spacing right in mathematical formulas.
In the previous paragraph we had to use the \verb/~/ symbol to 
manually insert a space between each number and its units.  The \verb/~/
symbol actually represents an unbreakable space, where \LaTeX\ will never
insert a line break. For occasional minor adjustments to the spacing
in a \LaTeX\ expression, you can insert or remove a little 
space with \verb/\,/ and \verb/\!/.  Use these macros sparingly,
because \LaTeX's default spacing rules will provide more consistency
within and among AJP articles.  The most common use of \verb/\,/ 
is in expressions like $T\,dS - P\,dV$.

\section{Displayed equations}
\label{DispEqSection}	% You can label sections for reference

When an equation is important and/or tall and/or complicated, you should 
display it on a line by itself, with a number. To do this, you put 
\verb/\begin{equation}/ before the equation and \verb/\end{equation}/ 
after it, as in     % Note: never put a blank line before an equation.
\begin{equation}
\int_0^\infty \! \frac{x^3}{e^x - 1} \, dx = 6\sum_{k=1}^\infty \frac1{k^4} = 
    6\left(\frac{\pi^4}{90}\right) = \frac{\pi^4}{15}.
\end{equation}
% Don't put a blank line after the equation unless you're starting a new paragraph.
This example also shows how to make the sum and integral symbols, big parentheses, 
% Don't use \left and \right for small parentheses; you'll get too much space around them.
and built-up fractions.  (Don't put built-up fractions in a 
non-displayed equation, because there won't be enough vertical space in 
AJP's final, single-spaced paragraphs.  Use the slashed form, $x^3/(e^x-1)$, 
instead.)

If you want to refer to an equation elsewhere in your manuscript, you can 
give it a label.  For example, in the equation
\begin{equation}
\label{deriv}
\frac{\Delta x}{\Delta t} \mathop{\longrightarrow}_{\Delta t\rightarrow0} \frac{dx}{dt} 
 = \lim_{\Delta t\rightarrow0} \frac{\Delta x}{\Delta t}
\end{equation}
we've inserted \verb/\label{deriv}/ to label this equation 
\texttt{deriv}.\cite{labelnames}  To refer to 
Eq.~(\ref{deriv}), we then type \verb/\ref{deriv}/.\cite{footnotes}  Notice 
that AJP's style conventions also require you to put the equation number in 
parentheses when you refer to it, and to abbreviate ``Eq.''\ unless it's at 
the beginning of a sentence.

Some equations require more complicated layouts. In the equation
\begin{equation}
E_n = (n + \tfrac12)\hbar, \quad \textrm{where}\  n = 0, 1, 2, \ldots,
\end{equation}
we've used \verb/\quad/ to leave a wide space and \verb/\textrm/ to put ``where'' 
in plain Roman type.  To create a matrix or column vector, as in
\begin{equation}
\begin{bmatrix}
	t' \\
	x' \\
\end{bmatrix}
=
\begin{pmatrix}
	 \gamma & -\beta\gamma \\
	-\beta\gamma & \gamma \\
\end{pmatrix}
\begin{bmatrix}
	t \\
	x \\
\end{bmatrix},
\end{equation}
you can use the \texttt{pmatrix} and/or \texttt{bmatrix} environment, 
for matrices delimited by parentheses and/or brackets.  There's also
a plain \texttt{matrix} environment that omits the delimiters.
In this and other examples of \LaTeX\ tables and arrays, the \verb/&/ 
character serves as a ``tab'' to separate columns, while the \verb/\\/ 
control sequence marks the end of a row.

For a list of related equations, with nicely lined-up equals signs, 
use the \texttt{eqnarray} environment:
\begin{eqnarray}
\oint \vec B \cdot d\vec\ell & = & -\frac{d\Phi_E}{dt} ; \\
\oint \vec E \cdot d\vec\ell & = & \mu_0\epsilon_0\frac{d\Phi_B}{dt} + \mu_0 I.
\end{eqnarray}
You can also use \texttt{eqnarray} to make a multi-line equation, for example,
\begin{eqnarray}
\mathcal{Z} 
& = & 1 + e^{-(\epsilon-\mu)/kT} + e^{-2(\epsilon-\mu)/kT} + \cdots \nonumber \\
& = & 1 + e^{-(\epsilon-\mu)/kT} + (e^{-(\epsilon-\mu)/kT})^2 + \cdots \nonumber \\
& = & \frac{1}{1 - e^{-(\epsilon-\mu)/kT}}.
\end{eqnarray}
Here the first column of the second and third lines is empty.  Note that you 
can use \verb/\nonumber/ within any line to suppress the generation of
an equation number; just be sure that each multi-line equation has at least 
one number.

Another commonly used structure is the \texttt{cases} environment, as in
\begin{equation}
m(T) =
\begin{cases}
	0 & T > T_c \, , \\
	\bigl(1 - [\sinh 2 \beta J]^{-4} \bigr)^{1/8} & T < T_c \, .
\end{cases}
\end{equation}

At AJP we require that you put correct punctuation before and after every
displayed equation, treating each equation as part of a correctly punctuated
English sentence.\cite{mermin} The preceding examples illustrate good
equation punctuation.

\section{Figures}

\LaTeX\ can import figures via the \verb/\includegraphics/ macro.
For AJP, you should embed this in the \texttt{figure} environment, which 
can place the figure in various locations.  This environment also lets 
you add a caption (which AJP requires) and an optional label for referring 
to the figure from elsewhere.  See Fig.~\ref{gasbulbdata} for an example.

\begin{figure}[h!]
% The bracketed code determines the figure's placement:  "h" stands for 
% "here", telling LaTeX to put the figure as close to the current location 
% as possible.  The ! overrides LaTeX's tendency to try to find a location 
% that it thinks is better.  But don't agonize over the exact figure placement 
% in your submitted manuscript.  For your initial submission, just make sure 
% each figure is reasonably close to where it's first referenced.
\centering
%\includegraphics{GasBulbData.eps}
\caption{Pressure as a function of temperature for a fixed volume of air.  
The three data sets are for three different amounts of air in the container. 
For an ideal gas, the pressure would go to zero at $-273^\circ$C.  (Notice
that this is a vector graphic, so it can be viewed at any scale without
seeing pixels.)}
\label{gasbulbdata}
\end{figure}
% When an AJP manuscript is conditionally accepted for publication, we
% will request an editable copy of the manuscript in which the figures 
% themselves have been removed, and all figure captions have been moved
% to the end.  You should then comment-out the \includegraphics line
% and move the entire \begin{figure} ... \end{figure} block to the end
% of the source file, just before \end{document}.

Most \LaTeX\ implementations can import a variety of graphics formats.
For graphs and line drawings you should use vector (i.e., resolution-independent)
graphics saved in encapsulated PostScript (.eps) or portable document
format (.pdf).  Most good graphics software systems can save to one 
or both of these formats.  Please don't use a rasterized graphics format
(such as .jpg or .png or .tiff) for graphs or line drawings.

\begin{figure}[h!]
\centering
%\includegraphics[width=5in]{ThreeSunsets.jpg}
% Notice the width specification.  Photographs should normally have a
% resolution of approximately 300 pixels per inch when printed, that is,
% a total width of about 1000 pixels for a photo to be printed one column
% wide.  Note also that this included photo is in .jpg format even though 
% a .tiff version should be submitted for final production.
\caption{Three overlaid sequences of photos of the setting sun, taken
near the December solstice (left), September equinox (center), and
June solstice (right), all from the same location at 41$^\circ$ north
latitude. The time interval between images in each sequence is approximately
four minutes.}
\label{sunsets}
\end{figure}

For photographs and other images that are \textit{inherently} made 
of pixels (that is, rasters or bitmaps), \LaTeX\ can 
(usually) handle the .jpg and .png formats as well as .eps and .pdf.  
Figure~\ref{sunsets} is a .jpg example. For final production, however, 
AJP prefers that raster images be in .tiff format.  Most \LaTeX\ systems 
can't import .tiff images, so we recommend using .png or .jpg with \LaTeX\ 
for your initial submission, while saving a higher-quality .tiff version 
to submit as a separate file after your manuscript is conditionally accepted
for publication.

Please refer to the AJP editor's web site\cite{editorsite} for more details 
on AJP's requirements for figure preparation.

\section{Tables}

Tables are somewhat similar to figures:  You use the \texttt{table} environment
to let them ``float'' to an appropriate location, and to automatically number
them and format their captions.  But whereas the content of a figure comes
from an external file, the content of a table is typeset directly in \LaTeX.
For that you use the \texttt{tabular} environment, which uses \verb/&/ and
\verb/\\/ for tabbing and ending rows, just like the \texttt{matrix} and
\texttt{eqnarray} environments discussed in Section~\ref{DispEqSection}.

Table~\ref{bosons} shows a fairly simple example.  Notice that the caption comes
before the table itself, so it will appear above the table instead of below.
The \texttt{ruledtabular} environment, which surrounds \texttt{tabular},
provides the double horizontal lines at the top and bottom, and stretches
the table horizontally out to the margins.  (This will look funny for tables
intended to fill only one column of a final journal page, but there's no 
need to worry about such cosmetic details.)

\begin{table}[h!]
\centering
\caption{Elementary bosons}
\begin{ruledtabular}
\begin{tabular}{l c c c c p{5cm}}
% The codes above determine the horizontal alignment in each column.
% Options are l (left), r (right), c (centered), and p (paragraph).
% The p option allows an entry to be broken into multiple lines, and
% therefore requires a width specification, in this case 5 centimeters.
Name & Symbol & Mass (GeV/$c^2$) & Spin & Discovered & Interacts with \\
\hline	% horizontal line to separate headings from data
Photon & $\gamma$ & \ \ 0 & 1 & 1905 & Electrically charged particles \\
Gluons & $g$ & \ \ 0 & 1 & 1978 & Strongly interacting particles (quarks and gluons) \\
Weak charged bosons & $W^\pm$ & \ 82 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$, $\gamma$ \\
Weak neutral boson & $Z^0$ & \ 91 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$ \\
Higgs boson & $H$ & 126 & 0 & 2012 & Massive particles (according to theory) \\
\end{tabular}
\end{ruledtabular}
\label{bosons}
\end{table}
% Tables, like figure captions, should be moved to the end when you submit 
% an editable manuscript for production, after conditional acceptance.
% Put the tables after the endnotes but before the figure captions.

Every table is a little bit different, and many tables will require
further tricks; see Refs.\ \onlinecite{wikibook} and~\onlinecite{latexbook}
for examples.  Note that the AJP style does not ordinarily use lines 
to separate rows and columns in the body of a table.

\section{Special formats}

\subsection{Block quotes}  % In subsection headings, only the first word is capitalized.

If a quoted passage is long or important, you can use the \texttt{quote} 
environment to typeset it as a block quote, as in this passage from The 
Feynman Lectures:\cite{feynman}
\begin{quote}
A poet once said, ``The whole universe is in a glass of wine.'' We will 
probably never know in what sense he meant that, for poets do not write 
to be understood. But it is true that if we look at a glass of wine closely 
enough we see the entire universe.
\end{quote}

\subsection{Numbered lists}

To create a numbered list, use the \texttt{enumerate} environment and start
each entry with the \verb/\item/ macro:
\begin{enumerate}
\item You can't win.
\item You can't even break even.
\item You can't get out of the game.
\end{enumerate}

\subsection{Unnumbered lists}

For a bulleted list, just use \texttt{itemize} instead of \texttt{enumerate}:
\begin{itemize}
\item Across a resistor, $\Delta V = \pm IR$.
\item Across a capacitor, $\Delta V = \pm Q/C$.
\item Across an inductor, $\Delta V = \pm L(dI/dt)$.
\end{itemize}

\subsection{Literal text}

For typesetting computer code, the \texttt{verbatim} environment reproduces
every character verbatim, in a typewriter font:
\begin{verbatim}
    u[t_] := NIntegrate[
        x^2 * Sqrt[x^2+t^-2] / (Exp[Sqrt[x^2+t^-2]] + 1), {x,0,Infinity}]
    f[t_] := NIntegrate[
        x^2 * Log[1+ Exp[-Sqrt[x2+t^-2]]], {x,0,Infinity}]
    Plot[((11Pi^4/90) / (u[t]+f[t]+(2Pi^4/45)))^(1/3), {t,0,3}]
\end{verbatim}
There's also a \verb/\verb/ macro for typesetting short snippets of verbatim
text within a paragraph. To use this macro, pick any character that doesn't
appear within the verbatim text to use as a delimiter. Most of the examples
in this article use \texttt{/} as a delimiter, but in \verb|{a/b}| we've used
\verb/|/ instead.

\section{Endnotes and references}

This article has already cited quite a few endnotes, using the \verb/\cite/
macro. See the end of this article (and source file) for the endnotes
themselves, which are in an environment called \texttt{thebibliography}
and are created with the \verb/\bibitem/ macro.  These macros require
you to give each endnote a name.  The notes will be numbered in the
order in which the \verb/\bibitem/ entries appear, and AJP requires that
this order coincide with the order in which the notes are first cited in 
the article.  You can cite multiple endnotes in a single \verb/\cite/, 
separating their names by commas.  And you can cite each note as many 
times as you like.

Notice that in the AJP (and Physical Review B) style, the citation numbers 
appear as superscripts. Think carefully about the optimal placement of
each citation, and try not to attach citations to math symbols where the
numbers might be misinterpreted as exponents. Often there will be a
punctuation symbol after the word where you attach the citation; you
should then put the citation \textit{after} the punctuation, not 
before.\cite{nevermindlogic}

If you want to refer directly to Ref.~\onlinecite{mermin} (or any other) 
in a sentence, you can do so with the \verb/\onlinecite/ macro.

Most endnotes consist of bibliographic citations.\cite{noBIBTeX}  Be sure 
to learn and use the AJP styles for citing books,\cite{latexbook} 
articles,\cite{dyson} edited volumes,\cite{examplevolume} and
URLs.\cite{latexsite}  For example, article titles are in double quotes, 
while book titles are in italics. Pay careful attention to all punctuation 
symbols in citations.  Note that AJP requires that all article citations 
include titles as well as beginning and ending page numbers.
Please use standard abbreviations, as listed in the AIP Style 
Manual,\cite{AIPstylemanual} for journal titles.

\section{Conclusion}

We hope this article will help you prepare beautifully typeset
manuscripts for the American Journal of Physics.  Good typesetting requires
considerable attention to detail, but this effort will pay off by making your
manuscript easier and more enjoyable to read.  Your colleagues, reviewers, 
and editors will be grateful for your effort.

Of course, we encourage you to put as much care into the \textit{content} 
of your manuscript as you put into its form.  The AIP Style 
Manual\cite{AIPstylemanual} is an indispensable reference on good physics 
writing, covering everything from planning and organization to standard 
spellings and abbreviations.

Most important of all, please familiarize yourself with the AJP Statement
of Editorial Policy,\cite{editorsite} which describes the types of manuscripts 
that AJP publishes and the audience for which AJP authors are expected to write.
You wouldn't want to put all that care into preparing a manuscript for AJP,
only to find that AJP is the wrong journal for your manuscript.

We look forward to receiving your submission to AJP.

\appendix*   % Omit the * if there's more than one appendix.

\section{Uninteresting stuff}

Appendices are for material that is needed for completeness but
not sufficiently interesting to include in the main body of the paper.  Most
articles don't need any appendices, but feel free to use them when
appropriate.  This sample article needs an appendix only to illustrate how 
to create an appendix.

\begin{acknowledgments}

We gratefully acknowledge Harvey Gould and Jan Tobochnik, who created an earlier 
AJP \LaTeX\ sample article that inspired this one.  This work was supported by the 
American Association of Physics Teachers.

\end{acknowledgments}

\begin{thebibliography}{99}
% The numeral (here 99) in curly braces is nominally the number of entries in
% the bibliography. It's supposed to affect the amount of space around the
% numerical labels, so only the number of digits should matter--and even that
% seems to make no discernible difference.

\bibitem{latexsite} \LaTeX\ Project Web Site, \url{<http://www.latex-project.org/>}.

\bibitem{wikibook} \textit{\LaTeX} (Wikibook), \url{<http://en.wikibooks.org/wiki/LaTeX/>}.

\bibitem{latexbook}Helmut Kopka and Patrick W. Daly, \textit{A Guide to
\LaTeX}, 4th edition (Addison-Wesley, Boston, 2004).

\bibitem{revtex} REV\TeX\ 4 Home Page, \url{<https://authors.aps.org/revtex4/>}.

\bibitem{cloudLaTeX} On the other hand, you can avoid the installation process
entirely by using a cloud-based \LaTeX\ processor such as ShareLaTeX,
\url{<https://www.sharelatex.com/>}, or write\LaTeX, \url{<https://www.writelatex.com/>}.

\bibitem{nevermindlogic} In typography, aesthetics often takes precedence over logic.

\bibitem{FontEncodingComment} Please don't try to handle foreign characters 
and accents with the \texttt{inputenc} and \texttt{fontenc} packages, which 
are incompatible with AJP's editing process.

\bibitem{wikimathpage} See the Mathematics chapter of Ref.~\onlinecite{wikibook}
for an excellent overview of math symbols and equations, with examples.

\bibitem{labelnames} Thinking up a good label name takes a moment, but 
it's worth the trouble; we strongly advise against using labels like 
\texttt{eq2}, which become extremely confusing after you decide to add 
another equation before Eq.~(\ref{deriv}).

\bibitem{footnotes} You need to process a file twice to get the counters correct.

\bibitem{mermin} N. David Mermin, ``What's wrong with these equations?,'' 
Phys. Today \textbf{42} (10), 9--11 (1989).  
% Note that the issue number (10) in this citation is required, because
% each issue of Physics Today starts over with page 1.  Also note the use of
% an en-dash (--), not a hyphen (-), for the page range.

\bibitem{editorsite} American Journal of Physics Editor's Web Site, 
\url{<http://ajp.dickinson.edu>}.

\bibitem{feynman} Richard P. Feynman, Robert B. Leighton, and Matthew Sands, 
\textit{The Feynman Lectures on Physics, Vol.\ 1} (Addison-Wesley, 1964), p.~3-10.
% Note that this book is paginated by chapter; "3-10" is a single page reference
% that uses a hyphen, not a range of pages that would us an en-dash (--).

\bibitem{noBIBTeX} Many \LaTeX\ users manage their bibliographic data with 
a tool called BIB\TeX.  Unfortunately, AJP cannot accept BIB\TeX\ files; all 
bibliographic references must be incorporated into the manuscript file
as shown here, at least when you send an editable file for production.

\bibitem{dyson} Freeman J. Dyson, ``Feynman's proof of the Maxwell equations,''
Am. J. Phys. \textbf{58} (3), 209--211.  
% The issue number (3) in this citation is optional, because AJP's pagination 
% is by volume.

\bibitem{examplevolume} M. R. Flannery, ``Elastic scattering,'' in 
\textit{Atomic, Molecular, and Optical Physics Handbook}, edited by
G. W. F. Drake (AIP Press, New York, 1996), p.~520.

\bibitem{AIPstylemanual} \textit{AIP Style Manual}, 4th edition (American 
Institute of Physics, New York, 1990). Available online at 
\url{<http://www.aip.org/pubservs/style/4thed/toc.html>}. Although parts of 
it have been made out of date by advancing technology, most of this manual 
is still as useful as ever. Just be sure to follow AJP's specific rules
whenever they conflict with those in the manual.

\end{thebibliography}

% If your manuscript is conditionally accepted, the editors will ask you to
% submit your editable LaTeX source file.  Before doing so, you should move
% all tables and figure captions to the end, as shown below.  Tables come 
% first, followed by figure captions (with figure inclusions commented-out).
% Figures should be submitted as separate files, collected with the
% LaTeX file into a single .zip archive.

%\newpage   % Start a new page for tables

%\begin{table}[h!]
%\centering
%\caption{Elementary bosons}
%\begin{ruledtabular}
%\begin{tabular}{l c c c c p{5cm}}
%Name & Symbol & Mass (GeV/$c^2$) & Spin & Discovered & Interacts with \\
%\hline
%Photon & $\gamma$ & \ \ 0 & 1 & 1905 & Electrically charged particles \\
%Gluons & $g$ & \ \ 0 & 1 & 1978 & Strongly interacting particles (quarks and gluons) \\
%Weak charged bosons & $W^\pm$ & \ 82 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$, $\gamma$ \\
%Weak neutral boson & $Z^0$ & \ 91 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$ \\
%Higgs boson & $H$ & 126 & 0 & 2012 & Massive particles (according to theory) \\
%\end{tabular}
%\end{ruledtabular}
%\label{bosons}
%\end{table}

%\newpage   % Start a new page for figure captions

%\section*{Figure captions}

%\begin{figure}[h!]
%\centering
%\includegraphics{GasBulbData.eps}   % This line stays commented-out
%\caption{Pressure as a function of temperature for a fixed volume of air.  
%The three data sets are for three different amounts of air in the container. 
%For an ideal gas, the pressure would go to zero at $-273^\circ$C.  (Notice
%that this is a vector graphic, so it can be viewed at any scale without
%seeing pixels.)}

%\label{gasbulbdata}
%\end{figure}

%\begin{figure}[h!]
%\centering
%\includegraphics[width=5in]{ThreeSunsets.jpg}   % This line stays commented-out
%\caption{Three overlaid sequences of photos of the setting sun, taken
%near the December solstice (left), September equinox (center), and
%June solstice (right), all from the same location at 41$^\circ$ north
%latitude. The time interval between images in each sequence is approximately
%four minutes.}
%\label{sunsets}
%\end{figure}

\end{document}

### 2014-11-19 Draft.tex
intro

@@
 % Section numbering is automatic.
-In 1911, certain types of metals at temperatures around 10 K were found to exhibit superconductivity, that is, their electrical resistance became zero. 
-The temperature at which this loss of resistance occurs is called the critical temperature.
+In 1911, Kamerlingh Onnes discovered superconductivity in mercury.  
+Instead of a gradual decrease in the electrical resistance as the temperature decreased, he found a sudden loss of resistance when the temperature went below 4.2 K. 
+The temperature at which the resistance disappears is called the critical temperature.
+In addition to having no resistance, superconductors also exhibit perfect diamagnetism, so it excludes magnetic field flux. 
+This property, called the Meissner effect, was found in 1933.
+
+%certain types of metals at temperatures around 10 K were found to exhibit superconductivity, that is, their electrical resistance became zero. 
+%The temperature at which this loss of resistance occurs is called the critical temperature.
 

### 2014-11-20 Draft.tex
intro

@@
 The temperature at which the resistance disappears is called the critical temperature.
-In addition to having no resistance, superconductors also exhibit perfect diamagnetism, so it excludes magnetic field flux. 
-This property, called the Meissner effect, was found in 1933.
+In addition to having no resistance, superconductors also exhibit perfect diamagnetism, which means they exclude all magnetic field flux from their interior. 
+This property, called the Meissner effect, was discovered in 1933.\cite{intro}
+A common demonstration of the Meissner effect is to place a a magnet on top of a superconductor above its critical temperature.
+When the superconductor is cooled to become superconducting, the magnet will start to levitate above the superconductor.
+This phenomenon can be used to make levitation trains.
+Superconductors are also used to create magnetic fields used in magnetic resonance imaging and in high energy physics to accelerate and control the path of particles.\cite{kumar}
+
+Superconductivity has been found to occur in elements, alloys, binary compounds, and other materials.  
+Roughly 70 years after superconductivity was discovered, ceramic materials with critical temperatures above the liquid nitrogen temperature of 77 K were found.\cite{melissinos} 
+These ``high temperature'' superconductors were made up of alternating layers of rare earth atoms and copper and oxygen atoms.\cite{kumar} In our experiment, we look at two high temperature superconductors, $\textrm{Yt}_{?}\textrm{Ba}_{?}\textrm{Cu}_{?}\textrm{O}_{?}$ and $\textrm{Bi}_{?}\textrm{Sr}_{?}\textrm{Ca}_{?}\textrm{Cu}_{?}\textrm{O}_{?}$.
 
@@
 
+\bibitem{intro} Charles Poole, Horacio Farach, and Richard Creswick, \textit{Superconductivity} (Academic Press, 2007).
+
+\bibitem{kumar} Ajay Kumar Saxena, \textit{High-Temperature Superconductors} (Springer Berlin Heidelberg, 2010).
+
+\bibitem{melissinos} Experiments in Modern Physics.  Adrian Constantin Melissinos and Jim Napolitano.  Gulf Professional Publishing, 2003
+
 \bibitem{latexsite} \LaTeX\ Project Web Site, \url{<http://www.latex-project.org/>}.

### 2014-11-21 Draft.tex
intro

@@
 
-%certain types of metals at temperatures around 10 K were found to exhibit superconductivity, that is, their electrical resistance became zero. 
-%The temperature at which this loss of resistance occurs is called the critical temperature.
+\section{Aims}
+\begin{enumerate}
+\item To determine the critical temperature of YBCO and BSCCO.
+\end{enumerate}
 
-\section{Ordinary text and paragraphs}
+\section{Procedure}
+The YBCO and BSCCO superconductors were obtained from Colorado Superconductor Inc.
+Each superconductor  is contained in a brass casing with two pairs of leads.
+One pair is attached to the current source and the other pair was used to measure voltage across the superconductor.
+The casing also contains a thermocouple, which has a resistance that varies with temperature.
+We measure the voltage across the thermocouple to find the temperature of superconductor.
+We used different methods to measure the critical temperature of the two superconductors.
 
+For the YBCO, we connected to an alternating current source of 1 mA. 
+\section{Results and Analysis}
+
+\section{Discussion}
+
+\section{Conclusion}
 To typeset a paragraph of ordinary text, just type the text in your source
@@
 hand will be really good at finding the backslash and curly-brace keys.
-
-\section{Math symbols}
 

### 2014-11-22 Draft.tex
intro/method

@@
 
-\title{Critical Temperature of Superconductors YBCO and BSCCO}
+\title{Critical Temperature of YBCO and BSCCO Superconductors}
 % In a long title you can use \\ to force a line break at a certain location.
@@
 \section{Procedure}
-The YBCO and BSCCO superconductors were obtained from Colorado Superconductor Inc.
-Each superconductor  is contained in a brass casing with two pairs of leads.
-One pair is attached to the current source and the other pair was used to measure voltage across the superconductor.
-The casing also contains a thermocouple, which has a resistance that varies with temperature.
-We measure the voltage across the thermocouple to find the temperature of superconductor.
+The YBCO and BSCCO superconductors were obtained from Colorado Superconductor Inc. Each superconductor  is contained in a brass casing with three pairs of leads. 
+One pair was for attaching to the current source, another pair was used to measure voltage across the superconductor, and the last pair that of the thermocouple inside the casing. 
+The thermocouple has a resistance that varies with temperature, so we can determine the  temperature of superconductor by measuring the voltage across the thermocouple.
+
 We used different methods to measure the critical temperature of the two superconductors.
-
-For the YBCO, we connected to an alternating current source of 1 mA. 
+For the YBCO, we connected it to a source with an alternating current of $\pm$1 mA.
+The voltage across the YBCO sample, $V_{\textrm{YBCO}}$, and the voltage across the thermocouple, $V_{T}$ were measured with two nanovoltmeters.
+We placed the supeconductor inside a styrofoam cup filled with sand.
+The sand reduces the rate at which the superconductor heats up, which allows us to gather more data points.
+We cooled the YBCO sample by pouring liquid nitrogen into the styrofoam cup.
+We monitored the thermocouple voltage to check when the temperature of the  sample settled to a minimum.
 \section{Results and Analysis}

### 2014-11-22 Draft.tex
method

@@
 The voltage across the YBCO sample, $V_{\textrm{YBCO}}$, and the voltage across the thermocouple, $V_{T}$ were measured with two nanovoltmeters.
-We placed the supeconductor inside a styrofoam cup filled with sand.
+We placed the superconductor inside a styrofoam cup filled with sand.
 The sand reduces the rate at which the superconductor heats up, which allows us to gather more data points. 
 We cooled the YBCO sample by pouring liquid nitrogen into the styrofoam cup.
-We monitored the thermocouple voltage to check when the temperature of the  sample settled to a minimum.
+We waited for the superconductor to settle to a minimum temperature.
+Then we recorded $V_{\textrm{YBCO}}$ and $V_{T}$ as it warmed up to above its critical temperature.
+
+We used a two-phase lock-in amplifier for the BSCCO experiment. This allows us to separate the resistance from any contributions from induction or capacitance.
+The BSCCO sample was connected in series with a 1 k$\Ohm$ resistor. This circuit was connected to a sinusoidal? voltage source with a RMS of 1 V. 
+Since the resistance of the BSCCO compared to the resistor is much smaller, even at room temperature, the current going through the circuit is approximately $\pm$1 mA.
+
 \section{Results and Analysis}
@@
 \section{Conclusion}
-To typeset a paragraph of ordinary text, just type the text in your source
-file like this. Put line breaks
-wherever
-you
-want, and don't      worry      about      extra      spaces      between      words, which \LaTeX\ will ignore.
-You can almost always trust \LaTeX\ to make your paragraphs look good, with neatly justified margins.
-% Long lines of text are fine, since most editing programs will wrap them automatically.
-
-To start a new paragraph, just leave a blank line in your source file.
-
-A few punctuation characters require special treatment in \LaTeX. There 
-are no ``smart quotes,'' so you need to use the left-quote key (at the 
-top-left corner of the keyboard) for a left quote, and the ordinary apostrophe
-key (next to the semi-colon) for a right quote. Hit either key twice for double
-quotes, which are standard in American English.  Don't use shift-apostrophe
-to make double quotes.  Use single quotes when they're nested inside a 
-double-quoted quotation.  When a period or comma belongs at the end of
-a quotation, put it inside the quotes---even if it's not part of what you're
-quoting.\cite{nevermindlogic}
-
-Your fingers also need to distinguish between a hyphen (used for
-multi-word adjectives and for hyphenated names like Lennard-Jones), an 
-en-dash (formed by typing two consecutive hyphens, and used for ranges 
-of numbers like 1--100), and an em-dash (formed out of three consecutive
-hyphens and used as an attention-getting punctuation symbol---preferably 
-not too often).
-
-Some non-alphanumeric symbols like \$, \&, and \% have special meanings 
-in a \LaTeX\ source file, so if you want these symbols to appear in the output, 
-you need to precede them with a backslash.
-
-There are also special codes for generating the various accents
-that can appear in foreign-language words and names, such as Amp\`ere
-and Schr\"odinger.\cite{FontEncodingComment}
-
-You can switch to \textit{italic}, \textbf{bold}, and \texttt{typewriter} fonts
-when necessary. Use curly braces to enclose the text that is to appear in 
-the special font. In general, \LaTeX\ uses curly braces to group characters 
-together for some common transformation.
-
-Notice that any word or symbol preceded by the backslash character is
-a special instruction to \LaTeX, typically used to produce a special 
-symbol or to modify the typeset output in some way. These instructions 
-are also called \textit{control sequences} or \textit{macros}.  
-After you've used \LaTeX\ for a while, the little finger of your right 
-hand will be really good at finding the backslash and curly-brace keys.
-
-To type mathematical symbols and expressions within a paragraph, put
-them between \$ signs, which indicate \textit{math mode}: $ab + 2c/d = e-3f$.
-\LaTeX\ ignores spaces in math mode, using its own algorithms to determine
-the right amount of space between symbols.  Notice that an ordinary letter 
-like~$x$, when used in math mode, is automatically typeset in italics. 
-This is why you need to use math mode for all mathematical
-expressions (except plain numerals), even when they don't contain any 
-special symbols.  But don't use math mode to italicize ordinary \textit{words}.
-
-Besides ordinary letters and numerals and common arithmetic symbols, math 
-mode provides a host of other characters that you can access via control 
-sequences.\cite{wikimathpage} These include Greek letters like $\pi$ and 
-$\Delta$ (note capitalization), symbols for operations and relations such 
-as $\cdot$, $\times$, $\pm$, $\gg$, $\leq$, $\sim$, $\approx$, $\propto$, 
-and $\rightarrow$, and special symbols like $\nabla$, $\partial$, $\infty$, 
-and~$\hbar$. You can decorate symbols with dots ($\dot x$ or $\ddot x$), 
-arrows ($\vec\mu$), bars ($\bar x$ or $\overline m$), hats ($\hat x$), 
-tildes ($\tilde f$ or $\widetilde w$), and radicals ($\sqrt\pi$, $\sqrt{2/3}$).
-Parentheses and square brackets require no special keystrokes, but you
-can also make curly braces and angle brackets: $\{\langle\ \cdots\ \rangle\}$.
-
-To make subscripts and superscripts, use the underscore and caret 
-(circumflex) symbols on your keyboard: $x^\mu$, $g_{\mu\nu}$, $\delta^i_j$, 
-$\epsilon^{ijk}$.  Notice that you need to put the subscript or superscript 
-in curly braces if it's longer than one character (or one control sequence). 
-You can even make nested subscripts and superscripts, as in $e^{-x^2}$.  
-If a subscript consists of an entire word or word-like abbreviation, 
-we usually put it in plain Roman type: $x_\textrm{max}$.  If you need to 
-put a subscript or superscript \textit{before} a symbol, use an empty
-set of curly braces: ${}^{235}_{\ 92}\textrm{U}$. (Notice the trick of using 
-backslash-space put a space before the 92.)
-
-\newcommand{\bE}{\mathbf{E}}   % defines the abbreviation \bE, used below
-
-To make boldface letters you use the \verb/\mathbf/ control sequence, as in
-$\nabla\times\mathbf{E} = -\partial\mathbf{B}/\partial t$.  For bold Greek
-letters like $\boldsymbol{\omega}$, you need to use \verb/\boldsymbol/
-instead.  You can also use calligraphic ($\mathcal{E}$), Fraktur 
-($\mathfrak{D}$), and blackboard bold ($\mathbb{R}$) fonts, if you need them. 
-If you'll be using a symbol in a special font repeatedly, you can save 
-some keystrokes by defining an abbreviation for it; for example, the 
-definition \verb/\newcommand{\bE}{\mathbf{E}}/ allows you to type simply 
-\verb/\bE/ to get $\bE$.
-
-Unit abbreviations, as in $1~\mathrm{eV} = 1.6\times10^{-19}~\mathrm{J}$,
-should be in the plain Roman font, not italics.  You can access this font
-from math mode using \verb/\mathrm/. For function names like $\sin\theta$, 
-$\exp x$, and $\ln N!$, \LaTeX\ provides special control sequences, 
-which you should use instead of \verb/\mathrm/ whenever possible because
-they work better with \LaTeX's automatic spacing algorithms.
-
-But \LaTeX\ doesn't always get the spacing right in mathematical formulas.
-In the previous paragraph we had to use the \verb/~/ symbol to 
-manually insert a space between each number and its units.  The \verb/~/
-symbol actually represents an unbreakable space, where \LaTeX\ will never
-insert a line break. For occasional minor adjustments to the spacing
-in a \LaTeX\ expression, you can insert or remove a little 
-space with \verb/\,/ and \verb/\!/.  Use these macros sparingly,
-because \LaTeX's default spacing rules will provide more consistency
-within and among AJP articles.  The most common use of \verb/\,/ 
-is in expressions like $T\,dS - P\,dV$.
-
-\section{Displayed equations}
-\label{DispEqSection}	% You can label sections for reference
-
-When an equation is important and/or tall and/or complicated, you should 
-display it on a line by itself, with a number. To do this, you put 
-\verb/\begin{equation}/ before the equation and \verb/\end{equation}/ 
-after it, as in     % Note: never put a blank line before an equation.
-\begin{equation}
-\int_0^\infty \! \frac{x^3}{e^x - 1} \, dx = 6\sum_{k=1}^\infty \frac1{k^4} = 
-    6\left(\frac{\pi^4}{90}\right) = \frac{\pi^4}{15}.
-\end{equation}
-% Don't put a blank line after the equation unless you're starting a new paragraph.
-This example also shows how to make the sum and integral symbols, big parentheses, 
-% Don't use \left and \right for small parentheses; you'll get too much space around them.
-and built-up fractions.  (Don't put built-up fractions in a 
-non-displayed equation, because there won't be enough vertical space in 
-AJP's final, single-spaced paragraphs.  Use the slashed form, $x^3/(e^x-1)$, 
-instead.)
-
-If you want to refer to an equation elsewhere in your manuscript, you can 
-give it a label.  For example, in the equation
-\begin{equation}
-\label{deriv}
-\frac{\Delta x}{\Delta t} \mathop{\longrightarrow}_{\Delta t\rightarrow0} \frac{dx}{dt} 
- = \lim_{\Delta t\rightarrow0} \frac{\Delta x}{\Delta t}
-\end{equation}
-we've inserted \verb/\label{deriv}/ to label this equation 
-\texttt{deriv}.\cite{labelnames}  To refer to 
-Eq.~(\ref{deriv}), we then type \verb/\ref{deriv}/.\cite{footnotes}  Notice 
-that AJP's style conventions also require you to put the equation number in 
-parentheses when you refer to it, and to abbreviate ``Eq.''\ unless it's at 
-the beginning of a sentence.
-
-Some equations require more complicated layouts. In the equation
-\begin{equation}
-E_n = (n + \tfrac12)\hbar, \quad \textrm{where}\  n = 0, 1, 2, \ldots,
-\end{equation}
-we've used \verb/\quad/ to leave a wide space and \verb/\textrm/ to put ``where'' 
-in plain Roman type.  To create a matrix or column vector, as in
-\begin{equation}
-\begin{bmatrix}
-	t' \\
-	x' \\
-\end{bmatrix}
-=
-\begin{pmatrix}
-	 \gamma & -\beta\gamma \\
-	-\beta\gamma & \gamma \\
-\end{pmatrix}
-\begin{bmatrix}
-	t \\
-	x \\
-\end{bmatrix},
-\end{equation}
-you can use the \texttt{pmatrix} and/or \texttt{bmatrix} environment, 
-for matrices delimited by parentheses and/or brackets.  There's also
-a plain \texttt{matrix} environment that omits the delimiters.
-In this and other examples of \LaTeX\ tables and arrays, the \verb/&/ 
-character serves as a ``tab'' to separate columns, while the \verb/\\/ 
-control sequence marks the end of a row.
-
-For a list of related equations, with nicely lined-up equals signs, 
-use the \texttt{eqnarray} environment:
-\begin{eqnarray}
-\oint \vec B \cdot d\vec\ell & = & -\frac{d\Phi_E}{dt} ; \\
-\oint \vec E \cdot d\vec\ell & = & \mu_0\epsilon_0\frac{d\Phi_B}{dt} + \mu_0 I.
-\end{eqnarray}
-You can also use \texttt{eqnarray} to make a multi-line equation, for example,
-\begin{eqnarray}
-\mathcal{Z} 
-& = & 1 + e^{-(\epsilon-\mu)/kT} + e^{-2(\epsilon-\mu)/kT} + \cdots \nonumber \\
-& = & 1 + e^{-(\epsilon-\mu)/kT} + (e^{-(\epsilon-\mu)/kT})^2 + \cdots \nonumber \\
-& = & \frac{1}{1 - e^{-(\epsilon-\mu)/kT}}.
-\end{eqnarray}
-Here the first column of the second and third lines is empty.  Note that you 
-can use \verb/\nonumber/ within any line to suppress the generation of
-an equation number; just be sure that each multi-line equation has at least 
-one number.
-
-Another commonly used structure is the \texttt{cases} environment, as in
-\begin{equation}
-m(T) =
-\begin{cases}
-	0 & T > T_c \, , \\
-	\bigl(1 - [\sinh 2 \beta J]^{-4} \bigr)^{1/8} & T < T_c \, .
-\end{cases}
-\end{equation}
-
-At AJP we require that you put correct punctuation before and after every
-displayed equation, treating each equation as part of a correctly punctuated
-English sentence.\cite{mermin} The preceding examples illustrate good
-equation punctuation.
-
-\section{Figures}
-
-\LaTeX\ can import figures via the \verb/\includegraphics/ macro.
-For AJP, you should embed this in the \texttt{figure} environment, which 
-can place the figure in various locations.  This environment also lets 
-you add a caption (which AJP requires) and an optional label for referring 
-to the figure from elsewhere.  See Fig.~\ref{gasbulbdata} for an example.
-
-\begin{figure}[h!]
-% The bracketed code determines the figure's placement:  "h" stands for 
-% "here", telling LaTeX to put the figure as close to the current location 
-% as possible.  The ! overrides LaTeX's tendency to try to find a location 
-% that it thinks is better.  But don't agonize over the exact figure placement 
-% in your submitted manuscript.  For your initial submission, just make sure 
-% each figure is reasonably close to where it's first referenced.
-\centering
-%\includegraphics{GasBulbData.eps}
-\caption{Pressure as a function of temperature for a fixed volume of air.  
-The three data sets are for three different amounts of air in the container. 
-For an ideal gas, the pressure would go to zero at $-273^\circ$C.  (Notice
-that this is a vector graphic, so it can be viewed at any scale without
-seeing pixels.)}
-\label{gasbulbdata}
-\end{figure}
-% When an AJP manuscript is conditionally accepted for publication, we
-% will request an editable copy of the manuscript in which the figures 
-% themselves have been removed, and all figure captions have been moved
-% to the end.  You should then comment-out the \includegraphics line
-% and move the entire \begin{figure} ... \end{figure} block to the end
-% of the source file, just before \end{document}.
-
-Most \LaTeX\ implementations can import a variety of graphics formats.
-For graphs and line drawings you should use vector (i.e., resolution-independent)
-graphics saved in encapsulated PostScript (.eps) or portable document
-format (.pdf).  Most good graphics software systems can save to one 
-or both of these formats.  Please don't use a rasterized graphics format
-(such as .jpg or .png or .tiff) for graphs or line drawings.
-
-\begin{figure}[h!]
-\centering
-%\includegraphics[width=5in]{ThreeSunsets.jpg}
-% Notice the width specification.  Photographs should normally have a
-% resolution of approximately 300 pixels per inch when printed, that is,
-% a total width of about 1000 pixels for a photo to be printed one column
-% wide.  Note also that this included photo is in .jpg format even though 
-% a .tiff version should be submitted for final production.
-\caption{Three overlaid sequences of photos of the setting sun, taken
-near the December solstice (left), September equinox (center), and
-June solstice (right), all from the same location at 41$^\circ$ north
-latitude. The time interval between images in each sequence is approximately
-four minutes.}
-\label{sunsets}
-\end{figure}
-
-For photographs and other images that are \textit{inherently} made 
-of pixels (that is, rasters or bitmaps), \LaTeX\ can 
-(usually) handle the .jpg and .png formats as well as .eps and .pdf.  
-Figure~\ref{sunsets} is a .jpg example. For final production, however, 
-AJP prefers that raster images be in .tiff format.  Most \LaTeX\ systems 
-can't import .tiff images, so we recommend using .png or .jpg with \LaTeX\ 
-for your initial submission, while saving a higher-quality .tiff version 
-to submit as a separate file after your manuscript is conditionally accepted
-for publication.
-
-Please refer to the AJP editor's web site\cite{editorsite} for more details 
-on AJP's requirements for figure preparation.
-
-\section{Tables}
-
-Tables are somewhat similar to figures:  You use the \texttt{table} environment
-to let them ``float'' to an appropriate location, and to automatically number
-them and format their captions.  But whereas the content of a figure comes
-from an external file, the content of a table is typeset directly in \LaTeX.
-For that you use the \texttt{tabular} environment, which uses \verb/&/ and
-\verb/\\/ for tabbing and ending rows, just like the \texttt{matrix} and
-\texttt{eqnarray} environments discussed in Section~\ref{DispEqSection}.
-
-Table~\ref{bosons} shows a fairly simple example.  Notice that the caption comes
-before the table itself, so it will appear above the table instead of below.
-The \texttt{ruledtabular} environment, which surrounds \texttt{tabular},
-provides the double horizontal lines at the top and bottom, and stretches
-the table horizontally out to the margins.  (This will look funny for tables
-intended to fill only one column of a final journal page, but there's no 
-need to worry about such cosmetic details.)
-
-\begin{table}[h!]
-\centering
-\caption{Elementary bosons}
-\begin{ruledtabular}
-\begin{tabular}{l c c c c p{5cm}}
-% The codes above determine the horizontal alignment in each column.
-% Options are l (left), r (right), c (centered), and p (paragraph).
-% The p option allows an entry to be broken into multiple lines, and
-% therefore requires a width specification, in this case 5 centimeters.
-Name & Symbol & Mass (GeV/$c^2$) & Spin & Discovered & Interacts with \\
-\hline	% horizontal line to separate headings from data
-Photon & $\gamma$ & \ \ 0 & 1 & 1905 & Electrically charged particles \\
-Gluons & $g$ & \ \ 0 & 1 & 1978 & Strongly interacting particles (quarks and gluons) \\
-Weak charged bosons & $W^\pm$ & \ 82 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$, $\gamma$ \\
-Weak neutral boson & $Z^0$ & \ 91 & 1 & 1983 & Quarks, leptons, $W^\pm$, $Z^0$ \\
-Higgs boson & $H$ & 126 & 0 & 2012 & Massive particles (according to theory) \\
-\end{tabular}
-\end{ruledtabular}
-\label{bosons}
-\end{table}
-% Tables, like figure captions, should be moved to the end when you submit 
-% an editable manuscript for production, after conditional acceptance.
-% Put the tables after the endnotes but before the figure captions.
-
-Every table is a little bit different, and many tables will require
-further tricks; see Refs.\ \onlinecite{wikibook} and~\onlinecite{latexbook}
-for examples.  Note that the AJP style does not ordinarily use lines 
-to separate rows and columns in the body of a table.
-
-\section{Special formats}
-
-\subsection{Block quotes}  % In subsection headings, only the first word is capitalized.
-
-If a quoted passage is long or important, you can use the \texttt{quote} 
-environment to typeset it as a block quote, as in this passage from The 
-Feynman Lectures:\cite{feynman}
-\begin{quote}
-A poet once said, ``The whole universe is in a glass of wine.'' We will 
-probably never know in what sense he meant that, for poets do not write 
-to be understood. But it is true that if we look at a glass of wine closely 
-enough we see the entire universe.
-\end{quote}
-
-\subsection{Numbered lists}
-
-To create a numbered list, use the \texttt{enumerate} environment and start
-each entry with the \verb/\item/ macro:
-\begin{enumerate}
-\item You can't win.
-\item You can't even break even.
-\item You can't get out of the game.
-\end{enumerate}
-
-\subsection{Unnumbered lists}
-
-For a bulleted list, just use \texttt{itemize} instead of \texttt{enumerate}:
-\begin{itemize}
-\item Across a resistor, $\Delta V = \pm IR$.
-\item Across a capacitor, $\Delta V = \pm Q/C$.
-\item Across an inductor, $\Delta V = \pm L(dI/dt)$.
-\end{itemize}
-
-\subsection{Literal text}
-
-For typesetting computer code, the \texttt{verbatim} environment reproduces
-every character verbatim, in a typewriter font:
-\begin{verbatim}
-    u[t_] := NIntegrate[
-        x^2 * Sqrt[x^2+t^-2] / (Exp[Sqrt[x^2+t^-2]] + 1), {x,0,Infinity}]
-    f[t_] := NIntegrate[
-        x^2 * Log[1+ Exp[-Sqrt[x2+t^-2]]], {x,0,Infinity}]
-    Plot[((11Pi^4/90) / (u[t]+f[t]+(2Pi^4/45)))^(1/3), {t,0,3}]
-\end{verbatim}
-There's also a \verb/\verb/ macro for typesetting short snippets of verbatim
-text within a paragraph. To use this macro, pick any character that doesn't
-appear within the verbatim text to use as a delimiter. Most of the examples
-in this article use \texttt{/} as a delimiter, but in \verb|{a/b}| we've used
-\verb/|/ instead.
-
-\section{Endnotes and references}
-
-This article has already cited quite a few endnotes, using the \verb/\cite/
-macro. See the end of this article (and source file) for the endnotes
-themselves, which are in an environment called \texttt{thebibliography}
-and are created with the \verb/\bibitem/ macro.  These macros require
-you to give each endnote a name.  The notes will be numbered in the
-order in which the \verb/\bibitem/ entries appear, and AJP requires that
-this order coincide with the order in which the notes are first cited in 
-the article.  You can cite multiple endnotes in a single \verb/\cite/, 
-separating their names by commas.  And you can cite each note as many 
-times as you like.
-
-Notice that in the AJP (and Physical Review B) style, the citation numbers 
-appear as superscripts. Think carefully about the optimal placement of
-each citation, and try not to attach citations to math symbols where the
-numbers might be misinterpreted as exponents. Often there will be a
-punctuation symbol after the word where you attach the citation; you
-should then put the citation \textit{after} the punctuation, not 
-before.\cite{nevermindlogic}
-
-If you want to refer directly to Ref.~\onlinecite{mermin} (or any other) 
-in a sentence, you can do so with the \verb/\onlinecite/ macro.
-
-Most endnotes consist of bibliographic citations.\cite{noBIBTeX}  Be sure 
-to learn and use the AJP styles for citing books,\cite{latexbook} 
-articles,\cite{dyson} edited volumes,\cite{examplevolume} and
-URLs.\cite{latexsite}  For example, article titles are in double quotes, 
-while book titles are in italics. Pay careful attention to all punctuation 
-symbols in citations.  Note that AJP requires that all article citations 
-include titles as well as beginning and ending page numbers.
-Please use standard abbreviations, as listed in the AIP Style 
-Manual,\cite{AIPstylemanual} for journal titles.
-
-\section{Conclusion}
-
-We hope this article will help you prepare beautifully typeset
-manuscripts for the American Journal of Physics.  Good typesetting requires
-considerable attention to detail, but this effort will pay off by making your
-manuscript easier and more enjoyable to read.  Your colleagues, reviewers, 
-and editors will be grateful for your effort.
-
-Of course, we encourage you to put as much care into the \textit{content} 
-of your manuscript as you put into its form.  The AIP Style 
-Manual\cite{AIPstylemanual} is an indispensable reference on good physics 
-writing, covering everything from planning and organization to standard 
-spellings and abbreviations.
-
-Most important of all, please familiarize yourself with the AJP Statement
-of Editorial Policy,\cite{editorsite} which describes the types of manuscripts 
-that AJP publishes and the audience for which AJP authors are expected to write.
-You wouldn't want to put all that care into preparing a manuscript for AJP,
-only to find that AJP is the wrong journal for your manuscript.
-
-We look forward to receiving your submission to AJP.
-
-\appendix*   % Omit the * if there's more than one appendix.
-
-\section{Uninteresting stuff}
-
-Appendices are for material that is needed for completeness but
-not sufficiently interesting to include in the main body of the paper.  Most
-articles don't need any appendices, but feel free to use them when
-appropriate.  This sample article needs an appendix only to illustrate how 
-to create an appendix.
-
-\begin{acknowledgments}
-
-We gratefully acknowledge Harvey Gould and Jan Tobochnik, who created an earlier 
-AJP \LaTeX\ sample article that inspired this one.  This work was supported by the 
-American Association of Physics Teachers.
-
-\end{acknowledgments}
 
@@
 \bibitem{melissinos} Experiments in Modern Physics.  Adrian Constantin Melissinos and Jim Napolitano.  Gulf Professional Publishing, 2003
-
-\bibitem{latexsite} \LaTeX\ Project Web Site, \url{<http://www.latex-project.org/>}.
-
-\bibitem{wikibook} \textit{\LaTeX} (Wikibook), \url{<http://en.wikibooks.org/wiki/LaTeX/>}.
-
-\bibitem{latexbook}Helmut Kopka and Patrick W. Daly, \textit{A Guide to
-\LaTeX}, 4th edition (Addison-Wesley, Boston, 2004).
-
-\bibitem{revtex} REV\TeX\ 4 Home Page, \url{<https://authors.aps.org/revtex4/>}.
-
-\bibitem{cloudLaTeX} On the other hand, you can avoid the installation process
-entirely by using a cloud-based \LaTeX\ processor such as ShareLaTeX,
-\url{<https://www.sharelatex.com/>}, or write\LaTeX, \url{<https://www.writelatex.com/>}.
-
-\bibitem{nevermindlogic} In typography, aesthetics often takes precedence over logic.
-
-\bibitem{FontEncodingComment} Please don't try to handle foreign characters 
-and accents with the \texttt{inputenc} and \texttt{fontenc} packages, which 
-are incompatible with AJP's editing process.
-
-\bibitem{wikimathpage} See the Mathematics chapter of Ref.~\onlinecite{wikibook}
-for an excellent overview of math symbols and equations, with examples.
-
-\bibitem{labelnames} Thinking up a good label name takes a moment, but 
-it's worth the trouble; we strongly advise against using labels like 
-\texttt{eq2}, which become extremely confusing after you decide to add 
-another equation before Eq.~(\ref{deriv}).
-
-\bibitem{footnotes} You need to process a file twice to get the counters correct.
-
-\bibitem{mermin} N. David Mermin, ``What's wrong with these equations?,'' 
-Phys. Today \textbf{42} (10), 9--11 (1989).  
-% Note that the issue number (10) in this citation is required, because
-% each issue of Physics Today starts over with page 1.  Also note the use of
-% an en-dash (--), not a hyphen (-), for the page range.
-
-\bibitem{editorsite} American Journal of Physics Editor's Web Site, 
-\url{<http://ajp.dickinson.edu>}.
-
-\bibitem{feynman} Richard P. Feynman, Robert B. Leighton, and Matthew Sands, 
-\textit{The Feynman Lectures on Physics, Vol.\ 1} (Addison-Wesley, 1964), p.~3-10.
-% Note that this book is paginated by chapter; "3-10" is a single page reference
-% that uses a hyphen, not a range of pages that would us an en-dash (--).
-
-\bibitem{noBIBTeX} Many \LaTeX\ users manage their bibliographic data with 
-a tool called BIB\TeX.  Unfortunately, AJP cannot accept BIB\TeX\ files; all 
-bibliographic references must be incorporated into the manuscript file
-as shown here, at least when you send an editable file for production.
-
-\bibitem{dyson} Freeman J. Dyson, ``Feynman's proof of the Maxwell equations,''
-Am. J. Phys. \textbf{58} (3), 209--211.  
-% The issue number (3) in this citation is optional, because AJP's pagination 
-% is by volume.
-
-\bibitem{examplevolume} M. R. Flannery, ``Elastic scattering,'' in 
-\textit{Atomic, Molecular, and Optical Physics Handbook}, edited by
-G. W. F. Drake (AIP Press, New York, 1996), p.~520.
-
-\bibitem{AIPstylemanual} \textit{AIP Style Manual}, 4th edition (American 
-Institute of Physics, New York, 1990). Available online at 
-\url{<http://www.aip.org/pubservs/style/4thed/toc.html>}. Although parts of 
-it have been made out of date by advancing technology, most of this manual 
-is still as useful as ever. Just be sure to follow AJP's specific rules
-whenever they conflict with those in the manual.
 

### 2014-11-23 Draft.tex
method

@@
 Roughly 70 years after superconductivity was discovered, ceramic materials with critical temperatures above the liquid nitrogen temperature of 77 K were found.\cite{melissinos} 
-These ``high temperature'' superconductors were made up of alternating layers of rare earth atoms and copper and oxygen atoms.\cite{kumar} In our experiment, we look at two high temperature superconductors, $\textrm{Yt}_{?}\textrm{Ba}_{?}\textrm{Cu}_{?}\textrm{O}_{?}$ and $\textrm{Bi}_{?}\textrm{Sr}_{?}\textrm{Ca}_{?}\textrm{Cu}_{?}\textrm{O}_{?}$.
+These ``high temperature'' superconductors were made up of alternating layers of rare earth atoms and copper and oxygen atoms.\cite{kumar} 
+In our experiment, we look at two high temperature superconductors, $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{n-1}\textrm{Cu}_{n}\textrm{O}_{9}$.
+%n=3 mainly for colorado superconductor 110 Tc
 
@@
 
-We used a two-phase lock-in amplifier for the BSCCO experiment. This allows us to separate the resistance from any contributions from induction or capacitance.
-The BSCCO sample was connected in series with a 1 k$\Ohm$ resistor. This circuit was connected to a sinusoidal? voltage source with a RMS of 1 V. 
-Since the resistance of the BSCCO compared to the resistor is much smaller, even at room temperature, the current going through the circuit is approximately $\pm$1 mA.
+We used a two-phase lock-in amplifier for the BSCCO experiment. In an AC circuit, the measurement of resistance includes contributions from capacitors and inductors. 
+Although there are no explicit capacitors or inductors in our circuit, they are effectively present due to the electrical cables used. 
+The lock-in amplifier allows us to extract the resistance of superconductor from the other contributions because the resistance will be in phase with the signal, while the contributions of capacitors and inductors will be out of phase.
+Since the resistance of the BSCCO at room temperature is on the order of m$\Omega$s, we can get approximately $\pm$1 mA in the circuit by connecting the BSCCO in series with a 1 k$\Omega$ resistor, and with a AC voltage source of 1 V.
 

### 2014-11-25 Draft.tex
edits

@@
 \begin{abstract}
-This article explains and illustrates the use of \LaTeX\ in preparing manuscripts
-for submission to the American Journal of Physics (AJP). While it is not a
-comprehensive reference, we hope it will suffice for the needs of most
-AJP authors.
+Superconductors are materials that lose their electrical resistance  when they fall below a certain temperature.
+This is called the critical temperature.
+We determine the critical temperatures of two superconductors,  $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$, by measuring the voltage across the resistor as a function of temperature.
 \end{abstract}
@@
 These ``high temperature'' superconductors were made up of alternating layers of rare earth atoms and copper and oxygen atoms.\cite{kumar} 
-In our experiment, we look at two high temperature superconductors, $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{n-1}\textrm{Cu}_{n}\textrm{O}_{9}$.
+In our experiment, we look at two high temperature superconductors, $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$, where $\textrm{n}=1,2,\textrm{ or},3$.
 %n=3 mainly for colorado superconductor 110 Tc
+The amount of oxygen in $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ determines if the material will be superconducting.
+For $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$, the critical temperature is depends on the value of n.
 

### 2014-11-26 Draft.tex
updates and pics

@@
 
-\author{}
-\affiliation{}
+\author{Ed Lipchus}
+\affiliation{Hampshire College, Amherst, MA 01002}
 
@@
 
-\section{Discussion}
+First, to convert our thermocouple voltage into a usable temperature, we transcribed the chart provided in the Teachspin manual that came with the YBCO and BSCCO samples and and plotted temperature vs voltage (see Fig.
+\ref{TCplot}).
+While it was best fit piecemeal, a single curve was able to cover our temperature range, and we used that function to convert our thermocouple voltages in later fits.
+
+\begin{figure}[width=5in][h!]
+\centering
+\includegraphics{thermocouple_voltage_vs_temp.png}
+\caption{Figure 1: Plot of Temperature and thermocouple voltage transcribed from the Teachspin manual, with fit lines across different sections.}
+\label{TCplot}
+\end{figure}
+
+We gathered data across two warm-ups of the YBCO sample, the first at equal time intervals between points (see Fig.
+\ref{YBCOplot1}) and the second focusing on taking more points during the transition period than elsewhere (see Fig.
+\ref{YBCOplot2}).
+In order to determine the critical temperature, we found the point along the transition period that was exactly in between the trend line for resistance during non-superconductivity and the trend line for resistance during superconductivity, and noted the corresponding temperature.
+The error in our voltage readings was very low (on the order of 0.000005mV), so the larger element of error is looking at the width of the transition zone, which was defined between the first points to clearly deviate from the trend lines.
+This yielded results of a $T_C$ of 98.03K and 98.67K per trial, with a range of 91K to 100K and 94K to 101K, respectively.
+
+\begin{figure}[width=5in][h!]
+\centering
+\includegraphics{ybco_sand_warmup_116_resistance_vs_temp.png}
+\caption{Plot of resistance vs temperature for YBCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between.
+Data was gathered every 20 seconds during warm-up.}
+\label{YBCOplot1}
+\end{figure}
+
+\begin{figure}[width=5in][h!]
+\centering
+\includegraphics{ybco_sand_warmup_1111_resistance_vs_temp.png}
+\caption{Plot of resistance vs temperature for YBCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between.
+Data was gathered every 30 seconds until onset of superconductivity, then every couple seconds throughout the transition period.}
+\label{YBCOplot2}
+\end{figure}
+
+Next we looked at a sample of BSCCO gathered through the two-phase lock-in amplifier.
+Only one trial was performed, though data was gathered every 3 seconds for 3 hours.
+Once the data was plotted, the same procedure was used as with the YBCO sample to determine the critical temperature (see Fig.
+\ref{BSCCOplot1}).
+The critical temperature $T_C$ here was 110K, with a range of 101K to 119K.
+Of particular interest was the trend during the early pre-superconducting period.
+While certainly not truly ceasing to superconduct, there appeared to be some jumps in resistance during the superconductive phase, shown closely in Fig.
+\ref{BSCCOplot2}.
+On closer inspection, while there is clearly some upward trend and movement not seen in the YBCO sample, it is not clear enough to pinpoint any specific jumps.
+
+\begin{figure}[width=10mm][h!]
+\centering
+\includegraphics{bscco_resistance_vs_temperature.png}
+\caption{Plot of resistance vs temperature for BSCCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between.}
+\label{BSCCOplot1}
+\end{figure}
+
+\begin{figure}[width=3in][h!]
+\centering
+\includegraphics{bscco_superconductivity_close-up.png}
+\caption{Close up of the BSCCO sample warm-up during it superconductive phase. Irregularities are definitely present, but jumps are not clear.}
+\label{BSCCOplot2}
+\end{figure}
 
 \section{Conclusion}
+
+Superconductivity was clearly achieved in both the YBCO and the BSCCO samples, and their transition to being non-superconductive as their temperature increased was recorded.
+Graphical analysis yielded a critical temperature for YBCO of 98.35K $pm$ 7K and for BSCCO of 110K $pm$ 9K.
+According to the Teachspin manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error.
+The strange behavior seen during the end of the superconducting phase of the BSCCO sample may also have had to do with the fact that BSCCO can have two other critical temperatures.
+The general formula is $\textrm{Bi}_{2,1}\textrm{Sr}_{n+1}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{2n+4+\delta}$.
+While the sample we had was specified for $n=3$, it is quite possible that other variations were present in our sample, each with their own critical temperature: $T_C$ for $n=1$ is 80K and $T_C$ for $n=2$ is 90K.
+While we did not get as cold as 80K, we could be seeing some sections stop superconducting around 90K, alongside the already non-superconducting $n=1$ material, giving us a not truly flat superconducting zone.
 

### 2014-11-26 Draft.tex
fixed images in paper

@@
 
-\begin{figure}[width=5in][h!]
+\begin{figure}[h!]
 \centering
-\includegraphics{thermocouple_voltage_vs_temp.png}
+\includegraphics[width=7in]{thermocouple_voltage_vs_temp.png}
 \caption{Figure 1: Plot of Temperature and thermocouple voltage transcribed from the Teachspin manual, with fit lines across different sections.}
@@
 
-\begin{figure}[width=5in][h!]
+\begin{figure}[h!]
 \centering
-\includegraphics{ybco_sand_warmup_116_resistance_vs_temp.png}
+\includegraphics[width=7in]{ybco_sand_warmup_116_resistance_vs_temp.png}
 \caption{Plot of resistance vs temperature for YBCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between.
@@
 
-\begin{figure}[width=5in][h!]
+\begin{figure}[h!]
 \centering
-\includegraphics{ybco_sand_warmup_1111_resistance_vs_temp.png}
+\includegraphics[width=7in]{ybco_sand_warmup_1111_resistance_vs_temp.png}
 \caption{Plot of resistance vs temperature for YBCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between.
@@
 
-\begin{figure}[width=10mm][h!]
+\begin{figure}[h!]
 \centering
-\includegraphics{bscco_resistance_vs_temperature.png}
+\includegraphics[width=7in]{bscco_resistance_vs_temperature.png}
 \caption{Plot of resistance vs temperature for BSCCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between.}
@@
 
-\begin{figure}[width=3in][h!]
+\begin{figure}[h!]
 \centering
-\includegraphics{bscco_superconductivity_close-up.png}
+\includegraphics[width=7in]{bscco_superconductivity_close-up.png}
 \caption{Close up of the BSCCO sample warm-up during it superconductive phase. Irregularities are definitely present, but jumps are not clear.}

### 2014-12-04 Draft.tex
comments on abstract
an abstract isn’t a movie trailer or a teaser advertisement. It is a
short article that stands on its own. If you measured a value for the
critical temperature, tell us what you found it to be!

@@
 \usepackage{graphicx} % needed for figures
-
+\usepackage{color}
 \begin{document}
@@
 \begin{abstract}
+
+\textcolor{blue}{don't leave us guessing what your results are!
+An abstract should ``stand-alone'' containing the key information needed to know what was done, how it was done, and what your key results were.
+Your result wasn't that you discovered superconductivity, or that you measured the critical temperature.
+Your result is that you found it to be a particular value, and it either agreed or disagreed with previous reports in the literature, that it indicated your material was either single phase or multiple phase (if you saw multiple transitions) and that you were able confirm the phase(s) or not from the transition temperature(s).}
+
 Superconductors are materials that lose their electrical resistance  when they fall below a certain temperature.
 This is called the critical temperature.
-We determine the critical temperatures of two superconductors,  $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$, by measuring the voltage across the resistor as a function of temperature.
+We determine the critical temperatures of two superconductors,  $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$ \textcolor{magenta}{to be}$xx \pm yy K$ \textcolor{magenta}{and} $uu \pm vv K$\textcolor{magenta}{respectively}, by measuring the voltage across the resistor as a function of temperature.
+\textcolor{red}{This reads as if you just measured the voltage, without passing any current.
+That would be a measurement of thermoelectric voltage, as with a thermocouple.
+You actually determined the critical temperature by passing a known current through the sample, measured the resulting voltage drop across the sample to find the resistance, then looked to see when the resistance became zero.
+}
+
 \end{abstract}

### 2014-12-04 Draft.tex
additional comments

@@
 This is called the critical temperature.
-We determine the critical temperatures of two superconductors,  $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$ \textcolor{magenta}{to be}$xx \pm yy K$ \textcolor{magenta}{and} $uu \pm vv K$\textcolor{magenta}{respectively}, by measuring the voltage across the resistor as a function of temperature.
+We determine the critical temperatures of two superconductors,  $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$ \textcolor{magenta}{to be }$xx \pm yy \textrm{ K}$ \textcolor{magenta}{and } $uu \pm vv \textrm{ K}$\textcolor{magenta}{ respectively}, by measuring the voltage across the resistor as a function of temperature.
 \textcolor{red}{This reads as if you just measured the voltage, without passing any current.
@@
 You actually determined the critical temperature by passing a known current through the sample, measured the resulting voltage drop across the sample to find the resistance, then looked to see when the resistance became zero.
+Or reached the halfway point in the transition to zero.
+or some other criteria.
 }

### 2014-12-04 Draft.tex
comment on aims section

@@
 The amount of oxygen in $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ determines if the material will be superconducting.
-For $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$, the critical temperature is depends on the value of n.
+For $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$, the critical temperature \textcolor{red}{is depends} on the value of n.
 
 \section{Aims}
+\textcolor{blue}{you should either expand on this --- with more specific aims --- or leave this section out. One sentence does not justify a section!}
 \begin{enumerate}

### 2014-12-04 Draft.tex
comments on procedure.
Generally OK. Needs more detail (as does everything). Description of
why voltage drop occurs across a thermocouple junction is physically
wrong and needs revision.

@@
 One pair was for attaching to the current source, another pair was used to measure voltage across the superconductor, and the last pair that of the thermocouple inside the casing. 
-The thermocouple has a resistance that varies with temperature, so we can determine the  temperature of superconductor by measuring the voltage across the thermocouple.
+\textcolor{red}{The thermocouple has a resistance that varies with temperature}, so we can determine the  temperature of superconductor by measuring the voltage across the thermocouple.
+\textcolor{blue}{NOT a resistance measurement!
+If it were a resistance, it would require the application of a current to generate a voltage drop across it.
+See http://en.wikipedia.org/wiki/Thermocouple }
 
@@
 For the YBCO, we connected it to a source with an alternating current of $\pm$1 mA. 
-The voltage across the YBCO sample, $V_{\textrm{YBCO}}$, and the voltage across the thermocouple, $V_{T}$ were measured with two nanovoltmeters.
+The voltage across the YBCO sample, $V_{\textrm{YBCO}}$, and the voltage across the thermocouple \textcolor{magenta}{junction}, $V_{T}$ were measured with two nanovoltmeters.
+\textcolor{blue}{you should explain the point of reversing the current and how this helps more accurately determine the true }$\Delta V$ \textcolor{blue}{ across the sample.
+You should also explain how you go from voltage drop to resistance, even though it is a simple calculation, or that the instrument does that for you.
+Finally, didn't you do some measurements at other values of current?}
+
 We placed the superconductor inside a styrofoam cup filled with sand. 
@@
 
-We used a two-phase lock-in amplifier for the BSCCO experiment. In an AC circuit, the measurement of resistance includes contributions from capacitors and inductors. 
-Although there are no explicit capacitors or inductors in our circuit, they are effectively present due to the electrical cables used. 
-The lock-in amplifier allows us to extract the resistance of superconductor from the other contributions because the resistance will be in phase with the signal, while the contributions of capacitors and inductors will be out of phase.
-Since the resistance of the BSCCO at room temperature is on the order of m$\Omega$s, we can get approximately $\pm$1 mA in the circuit by connecting the BSCCO in series with a 1 k$\Omega$ resistor, and with a AC voltage source of 1 V.
+We used a two-phase lock-in amplifier for the BSCCO experiment.
+An AC circuit \textcolor{magenta}{set up for the} measurement of resistance \textcolor{magenta}{is also susceptible to (or includes) } contributions from \textcolor{magenta}{parasitic capacitances and inductances between wires and to ground (or capacitors and inductors)}.
+Although there are no explicit capacitors or inductors in our circuit, they are effectively present due to the electrical cables used \textcolor{magenta}{and construction of the circuit}. 
+The lock-in amplifier allows us to extract the resistance of superconductor from the other contributions because the resistance will be in phase with the \textcolor{red}{signal}, while the contributions of capacitors and inductors will be out of phase.
+\textcolor{blue}{the in phase component IS your signal.
+I think you mean that the voltage drop across the sample due to its resistance will be in phase with the applied ac voltage from the oscillator, but of course you can say this more succinctly}.
+Since the resistance of the BSCCO at room temperature is on the order of m$\Omega$s, we can generate \textcolor{magenta}{an AC current with an RMS amplitude of approximately} $\pm$1 mA in the circuit by connecting the BSCCO in series with a 1 k$\Omega$ resistor, and with a AC voltage source \textcolor{magenta}{with an RMS amplitude} of 1 V.
 

### 2014-12-04 Draft.tex
first half of comments on results

@@
 
-First, to convert our thermocouple voltage into a usable temperature, we transcribed the chart provided in the Teachspin manual that came with the YBCO and BSCCO samples and and plotted temperature vs voltage (see Fig.
+First, to convert our thermocouple voltage into a usable temperature, we transcribed the chart provided in the \textcolor{red}{Teachspin manual}\textcolor{green}{Colorado Superconductor Inc} that came with the YBCO and BSCCO samples and and plotted temperature vs voltage (see Fig.
 \ref{TCplot}).
@@
 \includegraphics[width=7in]{thermocouple_voltage_vs_temp.png}
-\caption{Figure 1: Plot of Temperature and thermocouple voltage transcribed from the Teachspin manual, with fit lines across different sections.}
+\caption{Figure 1: \textcolor{blue}{PROOFREAD!} Plot of Temperature and thermocouple voltage transcribed from the \textcolor{red}{Teachspin manual}\textcolor{green}{Colorado Superconductor Inc} , with fit lines across different sections.}
 \label{TCplot}
@@
 \ref{YBCOplot2}).
-In order to determine the critical temperature, we found the point along the transition period that was exactly in between the trend line for resistance during non-superconductivity and the trend line for resistance during superconductivity, and noted the corresponding temperature.
+
+In order to determine the critical temperature, we found the point along the transition period that was \textcolor{red}{exactly in between}\textcolor{blue}{do you mean halfway between?} the trend line for resistance during non-superconductivity and the trend line for resistance during superconductivity, and noted the corresponding temperature.
 The error in our voltage readings was very low (on the order of 0.000005mV), so the larger element of error is looking at the width of the transition zone, which was defined between the first points to clearly deviate from the trend lines.
 This yielded results of a $T_C$ of 98.03K and 98.67K per trial, with a range of 91K to 100K and 94K to 101K, respectively.
+
+\textcolor{blue}{does this mean your first transition occurs at }$T_C = 98.0 \pm 4.5 \textrm{ K}$ \textcolor{blue}{ or that the transition begins at 91 K, ends at 100 K, and has a midpoint at 98 K?
+If the latter, what do you take to be the uncertainty in your determination of that midpoint?
+}
 

### 2014-12-04 Draft.tex
comments on analysis
missing section on critical current data and results

@@
 
-\textcolor{blue}{does this mean your first transition occurs at }$T_C = 98.0 \pm 4.5 \textrm{ K}$ \textcolor{blue}{ or that the transition begins at 91 K, ends at 100 K, and has a midpoint at 98 K?
+\textcolor{red}{does this mean your first transition occurs at }$T_C = 98.0 \pm 4.5 \textrm{ K}$ \textcolor{red}{ or that the transition begins at 91 K, ends at 100 K, and has a midpoint at 98 K?
 If the latter, what do you take to be the uncertainty in your determination of that midpoint?
+Also, you mention two trials, but only show one.
+Finally, why 4 sig figs for the critical temperature, if your uncertainty is on the order of 0.5 to 4.5 K, depending on how you define it.
 }
+\textcolor{blue}{That said, I like the method used to find the 1/2 way point (by drawing a line with 1/2 the slope seen in the resistive state).
+If you don't yet have a criteria for uncertainty for that value, one common definition is from 10 percent to 90 percent.
+So you could plot lines with slopes that are 10 percent and 90 percent to find those boundry points.}
 
@@
 \end{figure}
+
+\textcolor{red}{where is your data on critical currents?
+You measured the transition for other current values as well.
+You should show the data, and then either extrapolate the current dependence to the zero current limit, or show your data doesn't show a current dependence for your range of values.
+There are two parameters of interest in regard to current dependence, by the way.
+One would be the critical temperature.
+The other would be the width of the transition (from zero to ``normal'' resistive state)}.
 
@@
 Superconductivity was clearly achieved in both the YBCO and the BSCCO samples, and their transition to being non-superconductive as their temperature increased was recorded.
-Graphical analysis yielded a critical temperature for YBCO of 98.35K $pm$ 7K and for BSCCO of 110K $pm$ 9K.
-According to the Teachspin manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error.
+Graphical analysis yielded a critical temperature for YBCO of \textcolor{red}{fix this:} 98.35K $pm$ 7K and for BSCCO of 110K $pm$ 9K.
+According to the \textcolor{red}{Teachspin} manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error.
 The strange behavior seen during the end of the superconducting phase of the BSCCO sample may also have had to do with the fact that BSCCO can have two other critical temperatures.
@@
 While the sample we had was specified for $n=3$, it is quite possible that other variations were present in our sample, each with their own critical temperature: $T_C$ for $n=1$ is 80K and $T_C$ for $n=2$ is 90K.
-While we did not get as cold as 80K, we could be seeing some sections stop superconducting around 90K, alongside the already non-superconducting $n=1$ material, giving us a not truly flat superconducting zone.
+\textcolor{blue}{what is your source for this information about Tc values for n  = 1, 2, and 3?} While we did not get as cold as 80K, we could be seeing some sections stop superconducting around 90K, alongside the already non-superconducting $n=1$ material, giving us a not truly flat superconducting zone.
 

### 2014-12-04 Draft.tex
final comments

@@
 % Section numbering is automatic.
-In 1911, Kamerlingh Onnes discovered superconductivity in mercury.  
+\textcolor{blue}{generally OK, but the primary application of SC these days is actually to make high field magnets from superconducting wire, typically up to 18 or 20 tesla.
+This would be more relevant than levitating trains, which don't yet exist in commerical operation.} In 1911, Kamerlingh Onnes discovered superconductivity in mercury.
 Instead of a gradual decrease in the electrical resistance as the temperature decreased, he found a sudden loss of resistance when the temperature went below 4.2 K. 
@@
 For $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$, the critical temperature \textcolor{red}{is depends} on the value of n.
+\textcolor{magenta}{and these values are ?, according to ?
+source}.
 
@@
 You should also explain how you go from voltage drop to resistance, even though it is a simple calculation, or that the instrument does that for you.
-Finally, didn't you do some measurements at other values of current?}
+Include circuit diagrams.}
+
+\textcolor{red}{Finally, didn't you do some measurements at other values of current?
+for example, 10 mA and 100 mA, in addition to 1 mA?
+YOu were supposed to, and I thought you had.
+I can't find those results anywhere in your paper.
+}
 
@@
 
+\textcolor{red}{citations should include the ``teachspin'' manual (or the manual you really used) in addition to the 3 listed below. }
+
 \begin{thebibliography}{99}

### 2014-12-11 Draft.tex
edits

@@
 % Section numbering is automatic.
-\textcolor{blue}{generally OK, but the primary application of SC these days is actually to make high field magnets from superconducting wire, typically up to 18 or 20 tesla.
-This would be more relevant than levitating trains, which don't yet exist in commerical operation.} In 1911, Kamerlingh Onnes discovered superconductivity in mercury.
+In 1911, Kamerlingh Onnes discovered superconductivity in mercury.  
 Instead of a gradual decrease in the electrical resistance as the temperature decreased, he found a sudden loss of resistance when the temperature went below 4.2 K. 
@@
 When the superconductor is cooled to become superconducting, the magnet will start to levitate above the superconductor.
-This phenomenon can be used to make levitation trains.
-Superconductors are also used to create magnetic fields used in magnetic resonance imaging and in high energy physics to accelerate and control the path of particles.\cite{kumar}
+
+The main application of superconductors is in making high field magnets from superconducting wires.
+They can also be used to make levitation trains or to create magnetic fields used in magnetic resonance imaging and in high energy physics to accelerate and control the path of particles.\cite{kumar}
 
@@
 %n=3 mainly for colorado superconductor 110 Tc
-The amount of oxygen in $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ determines if the material will be superconducting.
-For $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$, the critical temperature \textcolor{red}{is depends} on the value of n.
+The amount of oxygen in $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ determines if the material will be superconducting.\cite{colorado} For $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$, the critical temperature \textcolor{red}{is depends} on the value of n.
 \textcolor{magenta}{and these values are ?, according to ?
@@
 One pair was for attaching to the current source, another pair was used to measure voltage across the superconductor, and the last pair that of the thermocouple inside the casing. 
-\textcolor{red}{The thermocouple has a resistance that varies with temperature}, so we can determine the  temperature of superconductor by measuring the voltage across the thermocouple.
-\textcolor{blue}{NOT a resistance measurement!
-If it were a resistance, it would require the application of a current to generate a voltage drop across it.
-See http://en.wikipedia.org/wiki/Thermocouple }
-
+The thermocouple produces a voltage when one part of the circuit has a temperature different from a reference point.
 We used different methods to measure the critical temperature of the two superconductors.
@@
 The voltage across the YBCO sample, $V_{\textrm{YBCO}}$, and the voltage across the thermocouple \textcolor{magenta}{junction}, $V_{T}$ were measured with two nanovoltmeters.
-\textcolor{blue}{you should explain the point of reversing the current and how this helps more accurately determine the true }$\Delta V$ \textcolor{blue}{ across the sample.
-You should also explain how you go from voltage drop to resistance, even though it is a simple calculation, or that the instrument does that for you.
-Include circuit diagrams.}
+\textcolor{blue}{you should explain the point of reversing the current and how this helps more accurately determine the true }$\Delta V$
+The voltage across the YBCO sample was converted into a resistance reading by the nanovoltmeter.
+ \textcolor{blue}{Include circuit diagrams.}
 
@@
 I think you mean that the voltage drop across the sample due to its resistance will be in phase with the applied ac voltage from the oscillator, but of course you can say this more succinctly}.
-Since the resistance of the BSCCO at room temperature is on the order of m$\Omega$s, we can generate \textcolor{magenta}{an AC current with an RMS amplitude of approximately} $\pm$1 mA in the circuit by connecting the BSCCO in series with a 1 k$\Omega$ resistor, and with a AC voltage source \textcolor{magenta}{with an RMS amplitude} of 1 V.
+Since the resistance of the BSCCO at room temperature is on the order of m$\Omega$s, we can generate an AC current with an RMS amplitude of approximately $\pm$1 mA in the circuit by connecting the BSCCO in series with a 1 k$\Omega$ resistor, and with a AC voltage source with an RMS amplitude of 1 V.
 
@@
 
+\bibitem{colo}
+
 \bibitem{melissinos} Experiments in Modern Physics.  Adrian Constantin Melissinos and Jim Napolitano.  Gulf Professional Publishing, 2003

### 2014-12-12 Draft.tex
edit methods

@@
 We used different methods to measure the critical temperature of the two superconductors.
-For the YBCO, we connected it to a source with an alternating current of $\pm$1 mA. 
-The voltage across the YBCO sample, $V_{\textrm{YBCO}}$, and the voltage across the thermocouple \textcolor{magenta}{junction}, $V_{T}$ were measured with two nanovoltmeters.
+For the YBCO, we connected it to a source with an alternating current of $\pm$1 mA. The alternating current  
+The voltage across the YBCO sample, $V_{\textrm{YBCO}}$, and the voltage across the thermocouple junction, $V_{T}$ were measured with two nanovoltmeters.
 \textcolor{blue}{you should explain the point of reversing the current and how this helps more accurately determine the true }$\Delta V$
@@
 
-We used a two-phase lock-in amplifier for the BSCCO experiment.
-An AC circuit \textcolor{magenta}{set up for the} measurement of resistance \textcolor{magenta}{is also susceptible to (or includes) } contributions from \textcolor{magenta}{parasitic capacitances and inductances between wires and to ground (or capacitors and inductors)}.
-Although there are no explicit capacitors or inductors in our circuit, they are effectively present due to the electrical cables used \textcolor{magenta}{and construction of the circuit}. 
-The lock-in amplifier allows us to extract the resistance of superconductor from the other contributions because the resistance will be in phase with the \textcolor{red}{signal}, while the contributions of capacitors and inductors will be out of phase.
-\textcolor{blue}{the in phase component IS your signal.
-I think you mean that the voltage drop across the sample due to its resistance will be in phase with the applied ac voltage from the oscillator, but of course you can say this more succinctly}.
+We used a two-phase lock-in amplifier for the BSCCO experiment. An AC circuit set up for the measurement of resistance is susceptible to contributions from capacitors and inductors. 
+Although there are no explicit capacitors or inductors in our circuit, they are effectively present due to the electrical cables used and construction of the circuit. 
+The lock-in amplifier allows us to extract the resistance of superconductor from the other contributions.
+Since changes in $V_{BSCCO}$ due to resistance are in phase with applied voltage and the contributions of capacitors and inductors are out of phase, our signal is just the in phase component.
 Since the resistance of the BSCCO at room temperature is on the order of m$\Omega$s, we can generate an AC current with an RMS amplitude of approximately $\pm$1 mA in the circuit by connecting the BSCCO in series with a 1 k$\Omega$ resistor, and with a AC voltage source with an RMS amplitude of 1 V.

### 2014-12-12 Draft.tex
edit method/add citation

@@
 This is called the critical temperature.
-We determine the critical temperatures of two superconductors,  $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$ \textcolor{magenta}{to be }$xx \pm yy \textrm{ K}$ \textcolor{magenta}{and } $uu \pm vv \textrm{ K}$\textcolor{magenta}{ respectively}, by measuring the voltage across the resistor as a function of temperature.
+We determine the critical temperatures of two superconductors,  $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{n-1}\textrm{Cu}_{n}\textrm{O}_{2n+4}$ to be $xx \pm yy \textrm{ K}$ and $uu \pm vv \textrm{ K}$\textcolor{magenta}{ respectively}, by measuring the voltage across the resistor as a function of temperature.
 \textcolor{red}{This reads as if you just measured the voltage, without passing any current.
@@
 These ``high temperature'' superconductors were made up of alternating layers of rare earth atoms and copper and oxygen atoms.\cite{kumar} 
-In our experiment, we look at two high temperature superconductors, $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$, where $\textrm{n}=1,2,\textrm{ or},3$.
+In our experiment, we look at two high temperature superconductors, $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{n-1}\textrm{Cu}_{n}\textrm{O}_{2n+4}$, where $n=1,2,\textrm{ or },3$.
 %n=3 mainly for colorado superconductor 110 Tc
-The amount of oxygen in $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ determines if the material will be superconducting.\cite{colorado} For $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$, the critical temperature \textcolor{red}{is depends} on the value of n.
-\textcolor{magenta}{and these values are ?, according to ?
-source}.
-
-\section{Aims}
-\textcolor{blue}{you should either expand on this --- with more specific aims --- or leave this section out. One sentence does not justify a section!}
-\begin{enumerate}
-\item To determine the critical temperature of YBCO and BSCCO.
-\end{enumerate}
+The amount of oxygen in $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ determines if the material will be superconducting.\cite{colo} The critical temperature of $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ is roughly 93 K.\cite{ybcotemp}
+For $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{n-1}\textrm{Cu}_{n}\textrm{O}_{2n+4}$, the critical temperature depends on the value of n.  
+They are 20 K, 85 K, and 110 K, for $n=1,2,\textrm{ and }3$, respectively.\cite{temps}
 
@@
 We used different methods to measure the critical temperature of the two superconductors. 
-For the YBCO, we connected it to a source with an alternating current of $\pm$1 mA. The alternating current  
+For the YBCO, we connected it to a source with an alternating current of $\pm$1 mA.
+The alternating current provides a more accurate reading of the voltage across the sample, because it removes any offset the voltmeter may have.
 The voltage across the YBCO sample, $V_{\textrm{YBCO}}$, and the voltage across the thermocouple junction, $V_{T}$ were measured with two nanovoltmeters. 
-\textcolor{blue}{you should explain the point of reversing the current and how this helps more accurately determine the true }$\Delta V$
 The voltage across the YBCO sample was converted into a resistance reading by the nanovoltmeter.
@@
 
-\bibitem{colo}
+\bibitem{colo} Experiment Guide for Superconductor Demonstrations. Colorado Superconductor Inc., Version 7.0, May 2007.
+
+\bibitem{ybcotemp} R.
+J.
+Cava, B.
+Batlogg, R.
+B.
+van Dover, D.
+W.
+Murphy, S.
+Sunshine, T.
+Siegrist, J.
+P.
+Remeika, E.
+A.
+Rietman, S.
+Zahurak, and G.
+P.
+Espinosa, "Bulk superconductivity at 91 K in sngle-phase oxygen-deficient perovskite $\textrm{Ba}_2\textrm{YCU}_3\textrm{O}_{9-\delta}$, Phys.
+Rev.
+Letters 58, 1676 (1987).
+
+\bibitem{temps} J.
+M.
+Tarascon, W.
+R.
+McKinnon, P.
+Barboux, D.
+M.
+Hwang, B.
+G.
+Bagley, L.
+H.
+Greene, G.
+W.
+Hull, Y.
+LePage, N.
+Stoffel, and M.
+Giroud, "Preparation, structure, and properties of the superconducting compound series $\textrm{Bi}_2\textrm{Sr}_2\textrm{Ca}_{n-1}\textrm{Cu}_{n}\textrm{O}_y$ with $n=1,2,\textrm{ and }3$", Phys.
+Rev.
+B 38, 8885 (1998).
 

### 2014-12-12 Draft.tex
edit abstract

@@
 This is called the critical temperature.
-We determine the critical temperatures of two superconductors,  $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{n-1}\textrm{Cu}_{n}\textrm{O}_{2n+4}$ to be $xx \pm yy \textrm{ K}$ and $uu \pm vv \textrm{ K}$\textcolor{magenta}{ respectively}, by measuring the voltage across the resistor as a function of temperature.
-\textcolor{red}{This reads as if you just measured the voltage, without passing any current.
-That would be a measurement of thermoelectric voltage, as with a thermocouple.
-You actually determined the critical temperature by passing a known current through the sample, measured the resulting voltage drop across the sample to find the resistance, then looked to see when the resistance became zero.
-Or reached the halfway point in the transition to zero.
-or some other criteria.
-}
+We determine the critical temperatures to be $xx \pm yy \text{ K}$ and $xx \pm yy \text{ K}$ for $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$.
+We find a single phase transition at $110\pm vv \text{ K}$ for $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$.
+The critical temperatures are found by passing a fixed current through the superconducting sample and measuring the change in voltage across the sample to determine its resistance. 
+We give the critical temperature as the temperature halfway through the transition from non-zero resistance to zero resistance.
+Previous measurement of the critical temperature for YBCO give a critical temperature of 91 K.
+Our critical temperature for BSCCO is in agreement with previous measurements for $n=3$ phase found in the literature.
+This confirms that our BSCCO consists of mainly $n=3$ as it was stated it the manual that came with our samples.
 
@@
 These ``high temperature'' superconductors were made up of alternating layers of rare earth atoms and copper and oxygen atoms.\cite{kumar} 
-In our experiment, we look at two high temperature superconductors, $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{n-1}\textrm{Cu}_{n}\textrm{O}_{2n+4}$, where $n=1,2,\textrm{ or },3$.
+In our experiment, we look at two high temperature superconductors, $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ and $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$, where $n=1,2,\text{ or },3$.
 %n=3 mainly for colorado superconductor 110 Tc
-The amount of oxygen in $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ determines if the material will be superconducting.\cite{colo} The critical temperature of $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ is roughly 93 K.\cite{ybcotemp}
-For $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{n-1}\textrm{Cu}_{n}\textrm{O}_{2n+4}$, the critical temperature depends on the value of n.  
-They are 20 K, 85 K, and 110 K, for $n=1,2,\textrm{ and }3$, respectively.\cite{temps}
+The amount of oxygen in $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ determines if the material will be superconducting.\cite{colo} The critical temperature of $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ is roughly 93 K.\cite{ybcotemp}
+For $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$, the critical temperature depends on the value of n.  
+They are 20 K, 85 K, and 110 K, for $n=1,2,\text{ and }3$, respectively.\cite{temps}
 
 \section{Procedure}
-The YBCO and BSCCO superconductors were obtained from Colorado Superconductor Inc. Each superconductor  is contained in a brass casing with three pairs of leads. 
+The YBCO and BSCCO superconductors were obtained from Colorado Superconductor Inc.
+The manual from Colorado Superconductor Inc.
+notes that the BSCCO samples consists of mainly $n=3$.
+Each superconductor  is contained in a brass casing with three pairs of leads.
 One pair was for attaching to the current source, another pair was used to measure voltage across the superconductor, and the last pair that of the thermocouple inside the casing. 
@@
 The alternating current provides a more accurate reading of the voltage across the sample, because it removes any offset the voltmeter may have.
-The voltage across the YBCO sample, $V_{\textrm{YBCO}}$, and the voltage across the thermocouple junction, $V_{T}$ were measured with two nanovoltmeters. 
+The voltage across the YBCO sample, $V_{\text{YBCO}}$, and the voltage across the thermocouple junction, $V_{T}$ were measured with two nanovoltmeters. 
 The voltage across the YBCO sample was converted into a resistance reading by the nanovoltmeter.
@@
 We waited for the superconductor to settle to a minimum temperature.
-Then we recorded $V_{\textrm{YBCO}}$ and $V_{T}$ as it warmed up to above its critical temperature.
+Then we recorded $V_{\text{YBCO}}$ and $V_{T}$ as it warmed up to above its critical temperature.
 
@@
 The lock-in amplifier allows us to extract the resistance of superconductor from the other contributions.
-Since changes in $V_{BSCCO}$ due to resistance are in phase with applied voltage and the contributions of capacitors and inductors are out of phase, our signal is just the in phase component.
+Since changes in $V_{\text{BSCCO}}$ due to resistance are in phase with applied voltage and the contributions of capacitors and inductors are out of phase, our signal is just the in phase component.
 Since the resistance of the BSCCO at room temperature is on the order of m$\Omega$s, we can generate an AC current with an RMS amplitude of approximately $\pm$1 mA in the circuit by connecting the BSCCO in series with a 1 k$\Omega$ resistor, and with a AC voltage source with an RMS amplitude of 1 V.
@@
 
-First, to convert our thermocouple voltage into a usable temperature, we transcribed the chart provided in the \textcolor{red}{Teachspin manual}\textcolor{green}{Colorado Superconductor Inc} that came with the YBCO and BSCCO samples and and plotted temperature vs voltage (see Fig.
+First, to convert our thermocouple voltage into a usable temperature, we transcribed the chart provided in the Colorado Superconductor Inc.
+experiment manual that came with the YBCO and BSCCO samples and and plotted temperature vs voltage (see Fig.
 \ref{TCplot}).
@@
 \includegraphics[width=7in]{thermocouple_voltage_vs_temp.png}
-\caption{Figure 1: \textcolor{blue}{PROOFREAD!} Plot of Temperature and thermocouple voltage transcribed from the \textcolor{red}{Teachspin manual}\textcolor{green}{Colorado Superconductor Inc} , with fit lines across different sections.}
+\caption{Figure 1: \textcolor{blue}{PROOFREAD!} Plot of Temperature and thermocouple voltage transcribed from the Colorado Superconductor Inc experiment manual, with fit lines across different sections.}
 \label{TCplot}
@@
 
-\textcolor{red}{does this mean your first transition occurs at }$T_C = 98.0 \pm 4.5 \textrm{ K}$ \textcolor{red}{ or that the transition begins at 91 K, ends at 100 K, and has a midpoint at 98 K?
+\textcolor{red}{does this mean your first transition occurs at }$T_C = 98.0 \pm 4.5 \text{ K}$ \textcolor{red}{ or that the transition begins at 91 K, ends at 100 K, and has a midpoint at 98 K?
 If the latter, what do you take to be the uncertainty in your determination of that midpoint?
@@
 The strange behavior seen during the end of the superconducting phase of the BSCCO sample may also have had to do with the fact that BSCCO can have two other critical temperatures.
-The general formula is $\textrm{Bi}_{2,1}\textrm{Sr}_{n+1}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{2n+4+\delta}$.
+The general formula is $\text{Bi}_{2,1}\text{Sr}_{n+1}\text{Ca}_{\text{n}-1}\text{Cu}_{\text{n}}\text{O}_{2n+4+\delta}$.
 While the sample we had was specified for $n=3$, it is quite possible that other variations were present in our sample, each with their own critical temperature: $T_C$ for $n=1$ is 80K and $T_C$ for $n=2$ is 90K.
@@
 P.
-Espinosa, "Bulk superconductivity at 91 K in sngle-phase oxygen-deficient perovskite $\textrm{Ba}_2\textrm{YCU}_3\textrm{O}_{9-\delta}$, Phys.
+Espinosa, "Bulk superconductivity at 91 K in sngle-phase oxygen-deficient perovskite $\text{Ba}_2\text{YCU}_3\text{O}_{9-\delta}$, Phys.
 Rev.
@@
 Stoffel, and M.
-Giroud, "Preparation, structure, and properties of the superconducting compound series $\textrm{Bi}_2\textrm{Sr}_2\textrm{Ca}_{n-1}\textrm{Cu}_{n}\textrm{O}_y$ with $n=1,2,\textrm{ and }3$", Phys.
+Giroud, "Preparation, structure, and properties of the superconducting compound series $\text{Bi}_2\text{Sr}_2\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_y$ with $n=1,2,\text{ and }3$", Phys.
 Rev.

### 2014-12-12 Draft.tex
cleaned up sections
Data, analysis, concl, and abstract fixed up as good as I think it can
get.

@@
 
-\textcolor{blue}{don't leave us guessing what your results are!
-An abstract should ``stand-alone'' containing the key information needed to know what was done, how it was done, and what your key results were.
-Your result wasn't that you discovered superconductivity, or that you measured the critical temperature.
-Your result is that you found it to be a particular value, and it either agreed or disagreed with previous reports in the literature, that it indicated your material was either single phase or multiple phase (if you saw multiple transitions) and that you were able confirm the phase(s) or not from the transition temperature(s).}
-
-Superconductors are materials that lose their electrical resistance  when they fall below a certain temperature.
-This is called the critical temperature.
-We determine the critical temperatures to be $xx \pm yy \text{ K}$ and $xx \pm yy \text{ K}$ for $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$.
-We find a single phase transition at $110\pm vv \text{ K}$ for $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$.
-The critical temperatures are found by passing a fixed current through the superconducting sample and measuring the change in voltage across the sample to determine its resistance. 
-We give the critical temperature as the temperature halfway through the transition from non-zero resistance to zero resistance.
-Previous measurement of the critical temperature for YBCO give a critical temperature of 91 K.
+Superconductors are materials that lose their electrical resistance when they fall below a certain temperature, called the critical temperature.
+We determined the critical temperatures for $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ to be $98.35\textrm{ K} \pm 7\textrm{ K}$.
+We found a single phase transition at $110\text{ K}\pm 9 \text{ K}$ for $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$ as well.
+The critical temperatures are found by passing a fixed current through a superconducting sample and measuring the change in voltage across the sample to determine its resistance.
+We describe the critical temperature as the temperature halfway through the transition from non-zero resistance to zero resistance.
+Previous measurement of the critical temperature for YBCO gives a critical temperature of 91 K.
 Our critical temperature for BSCCO is in agreement with previous measurements for $n=3$ phase found in the literature.
-This confirms that our BSCCO consists of mainly $n=3$ as it was stated it the manual that came with our samples.
+This confirms that our BSCCO consists of mainly $n=3$, as indicated in the manual that came with our samples.
+We also saw agreement with a gneral decrease in critical temperature with an increase in current run through the YBCO sample, however the transition was uneven and distorted, so a specific difference in critical temperature could not be determined.
 
@@
 \includegraphics[width=7in]{thermocouple_voltage_vs_temp.png}
-\caption{Figure 1: \textcolor{blue}{PROOFREAD!} Plot of Temperature and thermocouple voltage transcribed from the Colorado Superconductor Inc experiment manual, with fit lines across different sections.}
+\caption{Plot of temperature vs thermocouple voltage transcribed from the Colorado Superconductor Inc experiment manual, with fit lines across different sections.}
 \label{TCplot}
@@
 
-We gathered data across two warm-ups of the YBCO sample, the first at equal time intervals between points (see Fig.
+\begin{figure}[h!]
+\centering
+\includegraphics[width=7in]{i250_ma_plot_of_resistor_voltage_vs_temperature.png}
+\caption{Plot of resistor voltage vs temperature for a current of 250mA, with rebound effect representative of trials with currents above 1mA.}
+\label{ReboundPlot}
+\end{figure}
+
+To find a reasonable starting current, we ran warm up trials with currents of 250mA, 100mA, 50mA, and 1mA on the YBCO sample.
+For all voltages above 1mA, when analyzed the resistor voltage vs temperature graphs displayed a bizarre rebound effect where there would be an increase in resistance before a sudden and severe drop, then followed by an increase into non-superconductivity (see Fig \ref{ReboundPlot}).
+As a result, we took our main data using 1mA current.
+We gathered data at 1mA across two warm-ups of the YBCO sample, the first at equal time intervals between points (see Fig.
 \ref{YBCOplot1}) and the second focusing on taking more points during the transition period than elsewhere (see Fig.
@@
 
-In order to determine the critical temperature, we found the point along the transition period that was \textcolor{red}{exactly in between}\textcolor{blue}{do you mean halfway between?} the trend line for resistance during non-superconductivity and the trend line for resistance during superconductivity, and noted the corresponding temperature.
-The error in our voltage readings was very low (on the order of 0.000005mV), so the larger element of error is looking at the width of the transition zone, which was defined between the first points to clearly deviate from the trend lines.
-This yielded results of a $T_C$ of 98.03K and 98.67K per trial, with a range of 91K to 100K and 94K to 101K, respectively.
-
-\textcolor{red}{does this mean your first transition occurs at }$T_C = 98.0 \pm 4.5 \text{ K}$ \textcolor{red}{ or that the transition begins at 91 K, ends at 100 K, and has a midpoint at 98 K?
-If the latter, what do you take to be the uncertainty in your determination of that midpoint?
-Also, you mention two trials, but only show one.
-Finally, why 4 sig figs for the critical temperature, if your uncertainty is on the order of 0.5 to 4.5 K, depending on how you define it.
-}
-\textcolor{blue}{That said, I like the method used to find the 1/2 way point (by drawing a line with 1/2 the slope seen in the resistive state).
-If you don't yet have a criteria for uncertainty for that value, one common definition is from 10 percent to 90 percent.
-So you could plot lines with slopes that are 10 percent and 90 percent to find those boundry points.}
+In order to determine the critical temperature, we located the point along the transition period curve that was halfway between the trend line for resistance during non-superconductivity and the trend line for resistance during superconductivity, and noted the corresponding temperature.
+The error in our voltage readings was very low (on the order of 0.000005mV).
+The larger error contribution is related to the width of the transition zone.
+Defining the positive error as the temperature point where the resistance is at 90\% of the non-superconducting edge, and the negative error as the temperature point where the resistance is at 10\% of the non-superconducting edge, we obtained a range of  91K to 100K and 94K to 101K, for each trial respectively.
+This yields a final result of $T_{C}=98.03\textrm{K}\pm7\textrm{K}$ and $T_{C}=98.67\textrm{K}\pm4.67\textrm{K}$, respectively (using the greater of the positive and negative error to be conservative).
 
@@
 
-\textcolor{red}{where is your data on critical currents?
-You measured the transition for other current values as well.
-You should show the data, and then either extrapolate the current dependence to the zero current limit, or show your data doesn't show a current dependence for your range of values.
-There are two parameters of interest in regard to current dependence, by the way.
-One would be the critical temperature.
-The other would be the width of the transition (from zero to ``normal'' resistive state)}.
+\begin{figure}[h!]
+\centering
+\includegraphics[width=7in]{100ma_current_ybco_critical_temperature}
+\caption{Plot of resistor voltage vs temperature for a current of 100mA during transition from superconducting to non-superconducting.}
+\label{100mA}
+\end{figure}
+
+Despite troubles with rebound at higher currents, a video of the transition from superconducting to non-superconducting at a current of 100mA was obtained, and is shown in Fig \ref{100mA}.
+While the shaped following the rebound is distorted, and it is hard to identify a single point as the critical temperature – given the double curve effect – the 1mA YBCO trial is superconducting above 90K while the 100mA the sample has already begun the transition and has left pure superconducting by 90K.
 
@@
 \ref{BSCCOplot1}).
-The critical temperature $T_C$ here was 110K, with a range of 101K to 119K.
+The critical temperature $T_C$ here was 110K, with a range of 101K to 119K (10\% to 90\%) for an error of $\pm$ 9K.
 Of particular interest was the trend during the early pre-superconducting period.
@@
 Superconductivity was clearly achieved in both the YBCO and the BSCCO samples, and their transition to being non-superconductive as their temperature increased was recorded.
-Graphical analysis yielded a critical temperature for YBCO of \textcolor{red}{fix this:} 98.35K $pm$ 7K and for BSCCO of 110K $pm$ 9K.
-According to the \textcolor{red}{Teachspin} manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error.
+Graphical analysis yielded a critical temperature for YBCO of 98.35K $\pm$ 7K and for BSCCO of 110K $pm$ 9K.
+According to the Colorado Superconductor Inc manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error.
 The strange behavior seen during the end of the superconducting phase of the BSCCO sample may also have had to do with the fact that BSCCO can have two other critical temperatures.
@@
 While the sample we had was specified for $n=3$, it is quite possible that other variations were present in our sample, each with their own critical temperature: $T_C$ for $n=1$ is 80K and $T_C$ for $n=2$ is 90K.
-\textcolor{blue}{what is your source for this information about Tc values for n  = 1, 2, and 3?} While we did not get as cold as 80K, we could be seeing some sections stop superconducting around 90K, alongside the already non-superconducting $n=1$ material, giving us a not truly flat superconducting zone.
-
-\textcolor{red}{citations should include the ``teachspin'' manual (or the manual you really used) in addition to the 3 listed below. }
+\cite{colo} While we did not get as cold as 80K, we could be seeing some sections stop superconducting around 90K, alongside the already non-superconducting $n=1$ material, giving us a not truly flat superconducting zone.
+Finally, looking at the transition for YBCO with a current of 100mA, despite problems identifying a strict number for the critical temperature, the transition to non-superconducting clearly happens at a lower temperature then for 1mA.
+This is consistent with expectations since more energy from the increased current means that less thermal energy from warming up is needed to impart enough energy to stop the superconducting state within the YBCO crystals.
 

### 2014-12-13 Draft.tex
added pics

@@
 This confirms that our BSCCO consists of mainly $n=3$, as indicated in the manual that came with our samples. 
-We also saw agreement with a gneral decrease in critical temperature with an increase in current run through the YBCO sample, however the transition was uneven and distorted, so a specific difference in critical temperature could not be determined.
+We also saw agreement with a general decrease in critical temperature with an increase in current run through the YBCO sample, however the transition was uneven and distorted, so a specific difference in critical temperature could not be determined.
 
@@
 In our experiment, we look at two high temperature superconductors, $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ and $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$, where $n=1,2,\text{ or },3$.
-%n=3 mainly for colorado superconductor 110 Tc
 The amount of oxygen in $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ determines if the material will be superconducting.\cite{colo} The critical temperature of $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ is roughly 93 K.\cite{ybcotemp}
@@
 The voltage across the YBCO sample, $V_{\text{YBCO}}$, and the voltage across the thermocouple junction, $V_{T}$ were measured with two nanovoltmeters.
+Figure \ref{ybco} shows the setup for this experiment.
 The voltage across the YBCO sample was converted into a resistance reading by the nanovoltmeter.
- \textcolor{blue}{Include circuit diagrams.}
 
-\textcolor{red}{Finally, didn't you do some measurements at other values of current?
-for example, 10 mA and 100 mA, in addition to 1 mA?
-YOu were supposed to, and I thought you had.
-I can't find those results anywhere in your paper.
-}
+\begin{figure}
+\includegraphics[trim=1cm 3cm 1cm 1cm,clip=true,scale=0.6]{circuit1.png}
+\caption{A circuit diagram of the YBCO experiment.}
+\label{ybco}
+\end{figure}
 
@@
 
-We used a two-phase lock-in amplifier for the BSCCO experiment. An AC circuit set up for the measurement of resistance is susceptible to contributions from capacitors and inductors. 
+We used a two-phase lock-in amplifier for the BSCCO experiment, as shown in Figure \ref{bscco}.
+An AC circuit set up for the measurement of resistance is susceptible to contributions from capacitors and inductors.
 Although there are no explicit capacitors or inductors in our circuit, they are effectively present due to the electrical cables used and construction of the circuit. 
@@
 Since the resistance of the BSCCO at room temperature is on the order of m$\Omega$s, we can generate an AC current with an RMS amplitude of approximately $\pm$1 mA in the circuit by connecting the BSCCO in series with a 1 k$\Omega$ resistor, and with a AC voltage source with an RMS amplitude of 1 V.
+
+\begin{figure}
+\includegraphics[trim=0cm 0cm 0cm 1cm,clip=true,scale=0.6]{circuit2.png}
+\caption{A circuit diagram of the BSCCO experiment.}
+\label{bscco}
+\end{figure}
 
@@
 Defining the positive error as the temperature point where the resistance is at 90\% of the non-superconducting edge, and the negative error as the temperature point where the resistance is at 10\% of the non-superconducting edge, we obtained a range of  91K to 100K and 94K to 101K, for each trial respectively.
-This yields a final result of $T_{C}=98.03\textrm{K}\pm7\textrm{K}$ and $T_{C}=98.67\textrm{K}\pm4.67\textrm{K}$, respectively (using the greater of the positive and negative error to be conservative).
+This yields a final result of $T_{C}=98\pm7\textrm{K}$ and $T_{C}=99\textrm{K}\pm5\textrm{K}$, respectively (using the greater of the positive and negative error to be conservative).
 
-\begin{figure}[h!]
+Despite troubles with rebound at higher currents, a video of the transition from superconducting to non-superconducting at a current of 100mA was obtained, and is shown in Fig \ref{100mA}.
+While the shaped following the rebound is distorted, and it is hard to identify a single point as the critical temperatureâ given the double curve effectâ the 1mA YBCO trial is superconducting above 90K while the 100mA the sample has already begun the transition and has left pure superconducting by 90K.
+
+\begin{figure}[hb!]
 \centering
@@
 
-\begin{figure}[h!]
+\begin{figure}[hb!]
 \centering
@@
 \end{figure}
-
-Despite troubles with rebound at higher currents, a video of the transition from superconducting to non-superconducting at a current of 100mA was obtained, and is shown in Fig \ref{100mA}.
-While the shaped following the rebound is distorted, and it is hard to identify a single point as the critical temperature – given the double curve effect – the 1mA YBCO trial is superconducting above 90K while the 100mA the sample has already begun the transition and has left pure superconducting by 90K.
 
@@
 Superconductivity was clearly achieved in both the YBCO and the BSCCO samples, and their transition to being non-superconductive as their temperature increased was recorded.
-Graphical analysis yielded a critical temperature for YBCO of 98.35K $\pm$ 7K and for BSCCO of 110K $pm$ 9K.
+Graphical analysis yielded a critical temperature for YBCO of 98.35K $\pm$ 7K and for BSCCO of 110K $\pm$ 9K.
 According to the Colorado Superconductor Inc manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error.

### 2014-12-13 Draft.tex
added average comment
edit values

@@
 Superconductors are materials that lose their electrical resistance when they fall below a certain temperature, called the critical temperature.
-We determined the critical temperatures for $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ to be $98.35\textrm{ K} \pm 7\textrm{ K}$.
-We found a single phase transition at $110\text{ K}\pm 9 \text{ K}$ for $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$ as well.
+We determined the critical temperatures for $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ to be $98 \pm 7\textrm{ K}$.
+We found a single phase transition at $110 \pm 9 \text{ K}$ for $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$ as well.
 The critical temperatures are found by passing a fixed current through a superconducting sample and measuring the change in voltage across the sample to determine its resistance.
 We describe the critical temperature as the temperature halfway through the transition from non-zero resistance to zero resistance.
-Previous measurement of the critical temperature for YBCO gives a critical temperature of 91 K.
+Previous measurement of the critical temperature for YBCO from literature gives a critical temperature of 91 K.
+THe manual that came with our sample indicates a critical temperature of $92$ for $YBCO$.
+Both of these agree with the range we determined for the critical temperature.
 Our critical temperature for BSCCO is in agreement with previous measurements for $n=3$ phase found in the literature. 
-This confirms that our BSCCO consists of mainly $n=3$, as indicated in the manual that came with our samples. 
+This confirms that our BSCCO consists of mainly $n=3$, as indicated in the manual. 
 We also saw agreement with a general decrease in critical temperature with an increase in current run through the YBCO sample, however the transition was uneven and distorted, so a specific difference in critical temperature could not be determined.
@@
 
-\begin{figure}[hb!]
+\begin{figure}[h!]
 \centering
@@
 Superconductivity was clearly achieved in both the YBCO and the BSCCO samples, and their transition to being non-superconductive as their temperature increased was recorded.
-Graphical analysis yielded a critical temperature for YBCO of 98.35K $\pm$ 7K and for BSCCO of 110K $\pm$ 9K.
+Graphical analysis yielded a critical temperature for YBCO of 98 $\pm$ 7K and for BSCCO of 110K $\pm$ 9K.
 According to the Colorado Superconductor Inc manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error.
@@
 The general formula is $\text{Bi}_{2,1}\text{Sr}_{n+1}\text{Ca}_{\text{n}-1}\text{Cu}_{\text{n}}\text{O}_{2n+4+\delta}$.
-While the sample we had was specified for $n=3$, it is quite possible that other variations were present in our sample, each with their own critical temperature: $T_C$ for $n=1$ is 80K and $T_C$ for $n=2$ is 90K.
-\cite{colo} While we did not get as cold as 80K, we could be seeing some sections stop superconducting around 90K, alongside the already non-superconducting $n=1$ material, giving us a not truly flat superconducting zone.
+While the sample we had was specified for $n=3$, it is quite possible that $n=2$,  with a $T_C$ of 85K, were also present in our sample.
+\cite{colo} The fluctuations shown in Fig.
+\ref{BSCCOplot2} could be due to the $n=2$ compound, which stopped superconducting before the $n=3$ transition.
 Finally, looking at the transition for YBCO with a current of 100mA, despite problems identifying a strict number for the critical temperature, the transition to non-superconducting clearly happens at a lower temperature then for 1mA.

### 2014-12-13 Draft.tex

@@
 Superconductivity was clearly achieved in both the YBCO and the BSCCO samples, and their transition to being non-superconductive as their temperature increased was recorded.
-Graphical analysis yielded a critical temperature for YBCO of 98 $\pm$ 7K and for BSCCO of 110K $\pm$ 9K.
+Graphical analysis yielded a critical temperature for YBCO of 98 $\pm$ 7K (averaged between the two trials) and for BSCCO of 110K $\pm$ 9K.
 According to the Colorado Superconductor Inc manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error.
+Our values also agree with those found in the literature, 91 K for YBCO \cite{ybcotemp} and 110 K for $n=3$ BSCCO \cite{temps}.
 The strange behavior seen during the end of the superconducting phase of the BSCCO sample may also have had to do with the fact that BSCCO can have two other critical temperatures.
@@
 While the sample we had was specified for $n=3$, it is quite possible that $n=2$,  with a $T_C$ of 85K, were also present in our sample.
-\cite{colo} The fluctuations shown in Fig.
+The fluctuations shown in Fig.
 \ref{BSCCOplot2} could be due to the $n=2$ compound, which stopped superconducting before the $n=3$ transition.
